\begin{scenario}{All-Star Defence}
	{Bodyguard; Shadowing work}
	{Sport is a competitive world. The runners are out to ease the competition for their team}
	{Phantom Stranger}
	{2007-04-15}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7171978\#post7171978}

\johnson{Davey Rohr}{Seahawks} Davey Rohr, as he likes to be known, is a jovial human of about forty-six years of age; a former linebacker who had a couple years competition before his leg blew out, when he moved on to security. Now, over two decades later, he's back with the team that gave him his big shot, though he keeps the lowest profile he can; he's the executive interface between team, security, and the shadows. Sports is big business and you'd be surprised how many jobs they can't admit to.

\synopsis The Seahawks are looking to make the steal of the year---there's a troll running back coming up out the college leagues who covers ground like an elf. One of their scouts is bringing him in this coming Monday, they're wining and dining him for three days to swing him round. A number of other teams are very interested in preventing Joss Wallach from signing with the team, either to lure him away to their own side or simply to prevent him becoming a problem on the pitch. Playing in the rules, they can't make an approach; but their runners can. The PCs find themselves up against other runner crews being run close-in by Rohr's opposite numbers on the other teams over the three-day period. Their main advantage is that these runners will be going for extraction over killing---so far as Wallach's concerned, anyway. But they may well go for the kill if that's all they think they can get.

\notes I wrote the scenario as running five K retainer fee per PC per day plus one K per PC for every confirmed elimination of a non-Seahawk scout (not the runners, but their Johnsons). The main goal, however, was introducing the team to the idea that it isn't just the traditional corps who want to use runners and setting up a new contact. Think about the shit you hear people pulling related to big money sport even nowadays and I'm sure run ideas start pouring in; from drugging the water supply of a visiting team's hotel, preventing star players from making it to the game, the reverse of this scenario, down to a datasteal on a team's playbook codes... 

\end{scenario}