\begin{scenario}{Background Noise}
	{Intimidation; Bodyguarding?; Extraction?}
	{The shadowrunners are willing to take on big jobs for big nuyen, but will they be willing to clean up their own backyard?}
	{Devin Parker}
	{2009-02-07}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=9948465\#post9948465}

\johnson{Johnson}{Circumstance} 
No one hires the Shadowrunners to become involved. There is no payoff, no credsticks or street cred. This is something that plays out around them as they go about their profession. It's the background noise of the sprawl, and no one will ask them to become involved, except perhaps their consciences - if they still have those.

\synopsis One of the Shadowrunners lives in or near an apartment complex. One of the local residents is a teenaged Human girl who lives with her wageslave mother a door or two down from the PC. This mother can barely be dislodged from her simstims (and secret stash of BTLs) to be involved in the girl's life and a father who skipped out years ago but shows up occasionally for a booty call with Mom. Then, one day, the girl Goblinizes into an Ork. She ends up on the street - her mother can't cope with the change, the mood swings, the expressions of rage, the unpleasant appearance, and kicks her out. The girl ends up hooking up with an Ork gang, brought in by a new boyfriend who accepts her for who she is now - though he's terribly abusive and employs her in his petty criminal enterprises. First he gets her involved in acting as a lookout, keeping an eye peeled for Lone Star or rival gangs, but increasingly draws her deeper into more serious criminal activity. He gets her hooked on BTLs (which she previously swore she'd never touch, after seeing how it's affected her mother), she starts boosting cars, holding up stuffer shacks... Finally, her boyfriend becomes her pimp and starts renting her out. If the Shadowrunner(s) try to intervene, the boyfriend uses whatever resources he has to protect his ``investment,'' from rallying the other Ork gang members to intimidate and harrass the 'Runners, to gathering blackmail material on the 'Runners' illegal activities (either to turn over to Lone Star or to give to any enemies the PCs have made!). If the 'Runners are non-Orks, he claims racism as the PCs' motive for disrupting their activities, and tries to convince the local O.R.C. chapter to start putting pressure on the 'Runners, accusing them of being closet Humanis or something similar. And, of course, the girl herself is in denial about her dire situation, subconsciously feeling that she is of no worth and deserves all of the abuse she receives. If the 'Runners don't become involved, she continues to spiral downward, until one night after coming off a successful shadowrun they find her bruised and emaciated body sprawled out in the hallway, braindead and drooling with a BTL in her slot and drugs in her veins. There isn't enough left of her to attract even the organleggers...

\notes This is more of a character-driven subplot that can begin as mere window-dressing between runs. Every time a particular PC returns to his flat, he might run across gang members hanging around, witness a BTL sale, etc. The PC should see the girl at least once or twice as a Human before she Goblinizes. During the PCs' regular adventures, when the PC comes home, he might witness one further stage of the girl's devolution. It's up to the players to decide whether or not to become involved, but if they choose not to, they might feel at least partly responsible in the end for what happens... If the PCs do want to become involved, it'll be up to them how to help. This is an opportunity for the GM to introduce PCs to other local community figures, such as Mothers of Metahumans or other metahuman rights activist groups, churches running homeless shelters, squatter camps, organized crime groups who may be sponsoring the Ork gang's BTL sales, Lone Star patrollers (who could be either locals interested in cleaning up the neighborhood or crooked, on-the-take thugs), and so on. This could serve as a jumping-off point for numerous adventures that concern the state of their local community as well as helping the girl. Ork PCs might feel compelled to adopt the girl as a sort of little sister. Under the PCs' tutelage, she might discover talents she would never have found before - perhaps a talent with running the Matrix, or an affinity for machines...? 

\end{scenario}