\begin{scenario}{Back to Basic Training}
	{Infiltration}
	{The runners get to try out a cutting edge training facility before opening day, but things aren't that simple...}
	{Radendaren}
	{2007-04-15}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7172047#post7172047}

\johnson{Johnson}{Corporate Fixer} The Johnson is a fairly new fixer on the scene, and heavily under megacorp influence. He's fairly retro in look, mirror-shade eye covers and slick hair. He deals quickly, deeming the job to be straightforward, and emphasises the easiness of the mission in relation to the pay he's been authorized to offer.

\synopsis The runners are brought together to give a security corp's new training facility a test run before it goes live. The facility is organized in a hazard course style environment with physical tasks first, then combat, then specialist (hacking, bomb/electronics defusal, etc.). It becomes apparent that the facility has been sabotaged by a rival corp---and their team is still present in the control facility. The runners must escape the now-lethal complex alive, hopefully providing evidence of the saboteurs, or they may end up being blamed!

\notes This is a scenario I've run several times as an introduction to SR---getting players familiarised with rolling dice for various challenges. The exact details of the course can be left up to the GM's imagination; it could be a boot camp, or an urban combat zone simulation (complete with cardboard hostages and terrorists), or a shadowrunner training course (sneaky!). It's fun to mess with players' minds---let the sabotage be subtle at first, and then hit them with live ammunition and communications jamming. The saboteurs should ideally have been trying to set it up to place blame on the runners, but abort when the team arrives earlier than planned---so they try to take them out instead.

It works with any team makeup---just tailor the challenges to suit your characters. Give them plenty of options in dealing with escape---they could negociate with the saboteurs, or kill them all, or deactivate the jamming and call for backup from the Johnson, etc... 

\end{scenario}