\begin{scenario}{Better off Dead}
	{Extraction}
	{Loosely inspired by ``Better off Dead'' by Motorhead}
	{DeeCee}
	{2007-04-25}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7219106#post7219106}

\johnson{Johnson}{Go Ganger} Mo, a.k.a. Spicy MoMo, a.k.a. Sicktusks, a.k.a. Mother May I. A non-chromed human woman ganger that is rumoured to have beaten an orc street sam in a straight-up bar brawl. 'Nuff said? Even before the last Rumble, she had an edge in her eyes sharper than monofilament.

\synopsis The GM's favourite bunch of hellraisers just had a run-in with another group, quite literally. Twisted metal and bodies are about all that's left of a once-proud bunch, and they're calling in their markers for a last hurrah. If the PCs don't owe this go gang anything already, then they have plenty of motorcycles who now lack riders...

Mo was severely hurt in the last dust-up with the rival gang, and refuses to be taken to any proper medical facility. She knows they'd have to use chrome to fix her up, and that's not the way she wants to go out. She puts out the call for people to ride with the remnants of her gang, and they gear up to unleash hell one last time.

The 'run will be just that – fast and brutal. Mo is missing limbs, and has no time to mess about. Liberal application of meds and booze is keeping her going while the troops rally. The first part of the 'run calls for the PCs to get to Mo's location, and since the word is out, there are outrunners of the rival gang looking to prevent reinforcements from arriving.

The next stage means extracting Mo from her current location, and getting to a rendezvous with all of the people who are obliged to help her in her last trip. Not only will rival gang resistance be bad, but she's back of beyond and more than a little fiesty. Law enforcement and wannabes who don't know enough to stay out of her way will also be challenges.

The last stage is Mo's last hurrah. While the PCs might have paid off her debt or received motorcycles by now, should they go on the last run their street cred or notoriety will be raised accordingly. Her plan involves a frontal assault on what's left of the rival gang, with extinction on her mind. She should have pulled out all the stops by now – fire elementals, spirits of departed gang buddies, heavy artillery, and bloodied, surly bikers will all be along for the ride. Make their opposition tough (it's a fortified gang target they're hitting after all), but keep up the pace of a ride through hellfire and give your 'runners lots of chances at over-the-top vehicular glory. 

\end{scenario}