\begin{scenario}{A Black Comedy}
	{Numerous; Plot-Idea}
	{The screw job may not be overly realistic, but it happens all the time in SR games. This is the story of the aftermath of one such job...}
	{Jans}
	{2010-02-03}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=11636919#post11636919}

\johnson{Johnson}{None}  No specific Johnson other the PCs themselves and whoever they manage to con, bribe or blackmail.

\synopsis This was the screw-job of screw-jobs. The Runners are left with little but the clothes on their back after a serious burn by major players. They were ruined: No money, no gear, no contacts, no nothing. They might have even had their cyberware fried and/or magic suppressed. No one wants to talk to someone so clearly on the shit list of so many people. This would be the end of many runners....

But that's not the point here is it? A Black Comedy is an opportunity for your PCs to cut loose with all the tricks and trumps they've learned over their SR career in order to build themselves back up. It shouldn't feel like a punishment, it should feel like the opportunity to really hit the world that screwed them right where it hurts; the wallet.

\notes  A nod to Nonjon and the show Burn Notice for the idea that has been sitting in the back of my head for years now.

This scenario is for players who want to get out of the mold a bit. Like playing a high level evil campaign in D\&D, A Black Comedy would be an opportunity to ditch the system of Johnson, Run, and Runner to give your PCs a chance to grab the reins. It won't be for all groups, but there is a minority that will absolutely love it.

The fun part about A Black Comedy (for the GM at least) is how well it goes together with Those Who Hunt Thieves. If you're running with the same people (not necessarily the same characters, but the people themselves) who played TWHT, suddenly targeting and famous looks like a good idea. If you haven't run TWHT yet (or you want to run it again for a different set of people) you could use the PCs actions in ABC to drive that particular story as well. 

\end{scenario}