\begin{scenario}{Brain waves}
	{Retrieval}
	{Wouldn't it be great if we could take a look at that corp's product first?}
	{Sword Raven}
	{2007-04-15}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7173237#post7173237}

\johnson{Johnson}{Unspecified}  A street doctor, quite insane but with backing from a rival corporation, all he wants is his crowning glory of designing the latest cyberware for the discerning security team but he's a little stuck for ideas right now, perhaps with a bit of industrial espionage he could get his wish.

\synopsis Our street doc, he wants the 'runners to travel a short distance out of town to a small corp compound, it's known publicly as a research centre for leisure technologies including better simstim decks and pushing the boundaries of cold sims. Of course that's not what it really does. This site researches sensory enhancement cyberware for the security markets, allowing even simple patrols affordable means of boosting their effectiveness. This latest product is a bit of a macguffin, it does something vague that the doc will not describe to the runners as 'overly technical' and 'not something to worry about' but if pushed will reveal it is some sort of advanced communication device and will leave it there.

The plan is for the team to infiltrate the R\&D labs and retrieve the test subject of the new technology, a man in his mid-twenties. The research team at the compound are fanatical about their new development and will fight the 'runners as much as possible and at every step of the way. The subject must be returned alive as the technology is designed to self-destruct when vital signs stop being detected- preventing looting by ghouls or other chop shop operators.

Security at the site is relatively light, because it's true nature is well hidden from public knowledge (attempts to research the compound will meet with just the public face of the operation from all but the very best of sources) however, a larger security team is on 10-minute standby a short way away. They will arrive in unmarked black vans and do not bear any marks of the corp at all.

If the PCs are successful, the doc will take the young man from them and offer 5k nuyen each and become a low-level contact for each PC. However after a few contacts he will become pretty much useless, lost in his power fantasy.

\notes This is a really simple run except for the fact that your cargo is a living person. Who said he \textit{wants} to leave the compound? 

\end{scenario}