\begin{scenario}{Bunraku Breakout}
	{B\&E; Extraction}
	{Does the team have what it takes to break into a Yakuza owned Bunraku parlor and spirit away the daughter of a Mafia Don – without getting caught?}
	{Save vs DM}
	{2007-04-15}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7171841\#post7171841}

\johnson{Johnson}{Mafia} The Johnson is a well-dressed and heavy-set Italian man in his mid forties, with salt and pepper hair and a strong nose that looks like it’s been broken at least twice. He speaks in a slightly mumbled Italian accent, and looks every inch the Mafioso – because he is. He meets the team in a small Italian restaurant, even going so far as offering to buy them a nice pasta dinner over arrangements.

\synopsis It seems the local Yakuza kidnapped the wrong Mafia Don’s daughter to “work” in a Bunraku parlor. The Mafia Don is pissed at this affront to his family, and wants to make the Yakuza pay without getting involved himself. Using his extensive contacts, the Don has managed to locate the parlor his daughter was taken to, and also knows that she hasn’t yet been lobotomized. He hires the runners to extract his daughter, and any other Bunraku girl they can smuggle out, just to twist the knife a little. The runners are then to release a rather nasty virus that will wipe all of the data on the stored personality chips on the way out, putting the place out of business for good. The runners are provided with a basic layout of the area, a list of likely guards, and the virus – as well as a time limit of 24 hours. Beyond that, and the Don’s daughter is sure to have been lobotomized and put to work. He offers an excellent reward (double your standard reward), plus an additional 2,000 nuyen for every Bunraku girl smuggled out in addition to his daughter.
\notes  This is a time sensitive mission that works well for groups that are good at silent infiltration and speedy planning. A character who is skilled in hacking will be almost mandatory, though clever groups can either hire one for the job or find another way of implanting the virus. Successfully completing this mission might very well piss off the local Yakuza, but will definitely earn the favor of the local Mafia.

\end{scenario}