\begin{scenario}{Business is Good...A Little \textit{Too} Good...}
	{Investigation}
	{The runners play HR to help a street doc find staff.}
	{DeeCee}
	{2007-04-16}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7175545\#post7175545}

\johnson{Johnson}{Street Doc} Either a new contact street doc or one the PCs have known previously will seek them out. Actually, he'll pay some urchin to seek them out and arrange a meeting in his office. He's haggard and pressed for time, and his office is packed with people. The meeting takes place while he's actually working on some poor soul.

\synopsis The Johnson will tell the shadowrunners (as if it weren't obvious already) that his business has tripled in the last week, and is going way beyond shadow work. He'd rather give his whole body explosive-lined skin pockets than turn away business, but he's pushed to his breaking point and is worried his work and patients will begin to suffer.

He's offering the 'runners ten thousand nuyen if they can find a reliable assistant or two for him, two or three times that if they agree to take their payment in surgical work AND get him some time for a vacation.

Of course, finding an assistant for the doc won't be easy. They can lean on their contacts all they like, but word on the street is that all of the local Docs are being recruited by a new corporate face, and they're being sequestered while they attend to whatever duties the corporation has them doing.

Investigation into the corporation reveals that they are being fed a steady supply of high-end Activesofts, and the recruited docs are being paid well to set up the skillwire systems needed in the Corp's lackies.

\notes Finding an assistant for the Doc is easy enough, if the PCs travel far enough out of their local region. Really, the doc 'run is just a way to get them on the trail of the Activesofts and the new corporation. However, a GM might use the idea straight up to have the PCs finding or engineering a new assistant somehow. Note that most well-trained medical professionals don't turn into Street Docs, so they might need to find out what M.D.s are down on their luck enough to take the Johnson's offer. Failing that, they might find some local urchin who will agree to a Knowledgesoft implant in order o make some quick cash for proper medical training later. 

\end{scenario}
