\begin{scenario}{Cult Favourite}
	{Acquisition; Twist}
	{A rare manuscript shows up, and it looks like a simple job...}
	{Phantom Stranger}
	{2007-04-23}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7208372#post7208372}

\johnson{Johnson}{Media}  Joe Kinsella, a youngish ork from Cross Multimedia, likes to meet in cafes, preferably in burbclaves beyond the big cities. More used to dealing with literary agents than runners, he's profoundly nervous, takes copious notes on his PDA as he goes along, and buys everyone their favoured drinks and snacks. He tells them absolutely everything he knows.

\synopsis J.D. Salinger's final, unpublished manuscript was uncovered last week, and Limited Edition---a Seattle auction house---will be hosting the sale of rights. Kinsella ran the expected minimum selling price through his head, deducted the legal fees inherent in a steal, and came up with the price for the runners. LE's a big-name place with crappy security, relying on its name, elf-run. Guards are a mix of failed-to-get-into-LoneStar and washed-out-through-violent-tendencies, the latter half all being human. Investigation of the magical wards turns up a guy called Goat, an ethnically-Mexican human hermetic mage with some very odd behavioural habits and a thing for blood. He also runs a gang, an extremist splinter group of the Humanis Policlub. The runners should wonder what the hell he's doing working for an elf by the time they go in, at which point they're called with major information---Goat's planted a bomb in Limited Edition itself. The violent guards are all, on inspection, branded in the ankle with racist/hermetic glyphs, and assense as Influenced. They're packing high-ex rounds as well as stun, while the others just pack stun rounds.

\notes A basic run with a nasty twist. Useful for introducing darker (including blood) magics, foreshadowing dangerous Aztlan practices, and confronting the PCs with race hate. Obvious fallout includes Goat (who'll be offsite) and his gang, and the rush to fill their void if they're eliminated...

\end{scenario}