\begin{scenario}{Damien Knight and the Ammo Factory}
	{Unspecified}
	{TODO}
	{Bull}
	{2009-05-08}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=10333900#post10333900}

Damien Knight, the eccentric President and CEO of Ares Macrotechnology, has announced the unveiling of a new, state of the art munitions factory. The munitions factory will be the first factory completely run by a couple new semi-intelligent robots created by Ares for the creation and processing of munitions, the MPA (Munitions Protocol Androids) and the LMPA (Light Munitions Protocol Androids).

Opening early in the Fall will be Ares Ammo World, an adult oriented ``theme park'' where patrons can try out various weapons they may never be able to play with normally (Machine Guns, Lasers, Rockets, Explosives) and will have other Weapon Oriented games, rides, and attractions. The MPA LMPA's run every aspect of the factory and the park, their diminutive robotic forms scurrying about constantly behind the scenes.

To promote the new Weapon Factory and Park (collectively being called Ares Ammo World), Knight has also announced a contest being run to get a special ``sneak peek'' tour of Weapons World months in advance. Randomly inserted into boxes of heavy pistol ammo sold at Ares Arms, Weapons World, and other Ares Owned weapons stores are 6 Golden Bullets. Anyone finding one of these bullets wins not only a tour of the Ammo World park, guided by Knight himself, for the winner and up to 5 of his closest friends, but a lifetime supply of bullets, as well as any gun Ares makes to use those bullets in!

Hooks:

\subsection{Damien Knight Wants You!}

At some point in their past, the runners have run afoul of Ares and Knight, and it has somehow touched a nerve with the head of one of the most powerful corporations in the world. Maybe it was just that they stole (or ruined) a project that Knight had a personal interest in. Maybe that Knight Errant guard they shot and killed last year was Knight's 2nd Cousin. Either way, Knight is rather upset, and he's decided to have a little fun with the runners. After all, Damien likes his revenge slow and painful.

Welcome to Ammo World. Runners check in, but they don't check out.

\subsection{You're Not Paranoid. Everyone \textit{Is} Out to Get you!}

Finding the Golden Bullet is a MAJOR event in the news. Knight and Ares has been promoting the HELL out of this event, and unless the runners want to chuck (or sell off) this opportunity of a lifetime, they get a BIG news spotlight on them. Anyone who wants a shot at this prize may try to take the Golden Bullet from the runners by force, and any enemies who want to nail the runners to the wall may find the unmanned theme park a prime location to try and knock the players off.

You can run. You can hide. And there's plenty of Ammo to be had!

\subsection{Hi, My Name Is Mr. Johnson, And This Is A Golden Bullet...}

You've been hearing about this contest for weeks now. 5 of the Golden Bullets have been found, and just yesterday they discredited a 6th as a fake. So there's one left out there, and the newshounds are out in force looking for it. Unfortunately, the last box of ammo you bought only had the same 'ol APDS rounds it usually does. That's when Mr. Johnson calls, and hands you're team the 6th Golden Bullet.

The catch? Seems Ares has some Prototype Weapons lying around in that new factory of theirs. In exchange for the prize, as well as some cold, hard Nuyen, Mr. J wants those prototypes.

\subsection{Making Friends The Hard Way}

Damien Knight is VERY confident about the automated security in his new factory. TOO confident, in fact. Halfway through your tour of Ammo World, the automated security turns on it's creator, and it's up to you to get Damien out of this Robotic Hell in one piece, as well as the rest of the Tour Groups. After all, dead Tourists make for BAD PR, and Damien will be VERY grateful to the runners if they get them all out in one piece.

If only those damned MPA LMPA bots would quit SINGING!

\end{scenario}