\begin{scenario}{Debt in Hand}
	{Bodyguard; Intimidation}
	{Debt refinancing with the yakuza is complicated by an ancient artifact and Tir Tairngire Ghosts.}
	{Deacon Blues}
	{2007-04-15}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7173882\#post7173882}

\johnson{Johnson}{senator's Aide} 
An aide to Senator Thanh from the Seattle Senate. He's dealt with runners before, but he's not supremely comfortable around them.

\synopsis The Senator's son has been gambling at a couple of yakuza dens in town. Senator Thanh was recently presented with some IOUs signed by his son, with an accompanying request that he pay up---with interest---or the debts go to the press. Sen. Thanh doesn't want a scandal, but he doesn't want to come off as soft to the yakuza either. So he wants the runners to find out if the debt is legitimate and, if so, talk the yakuza into taking a smaller sum (less than the original debt, and not even counting the interest).

\twist In surveiling the Senator's kid, the runners will discover that he's actually got a remarkable winning streak going on. Every time he walks into a casino, he wins such a huge stash that he's accused of cheating or muscled out without getting his winnings. The boy hasn't won enough money in one night to pay off his IOUs (which are legit), but he could.

The problem is, he's not interested in those debts. He's trying to win enough money to buy out the contract of one of the yakuza ``pleasure girls,'' a Cindi Yee, whom he fell for in a hard way. Cindi's not in love with the boy, but she's a player. She knows a rich mark when she sees one, so she's not going to dissuade him.

The other problem is that his remarkable winning streak stems from his recent acquisition of an ancient, Fourth-World artifact (a large ring that he wears on a chain around his neck). And when a platoon of Tir Tairngire Ghosts shows up looking for the relic, who knows who'll get caught in the crossfire?

\notes  There's no set ending to how this plays out. Maybe the runners kill both the Ghosts and the yakuza, which will earn them powerful enemies. The runners could play the Ghosts and the yakuza off against each other and pick off the survivors. They might make a deal with one side or the other (e.g., ``Cancel Mickey Thanh's debts and we'll wipe out the elf commandos for you''). By the time the dust settles, they might be willing to pony up the 400,000 nuyen for the IOU themselves, just for the privilege of walking out alive. 

\end{scenario}
