\begin{scenario}{Dunk Tank}
	{Extraction; Possible Wetwork}
	{Runners are asked to ``deal with'' an ork bar's captive merrow.}
	{DeeCee}
	{2007-04-15}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7173573\#post7173573}

\johnson{Johnson}{Humanis}  Chances are that the 'runners will come into contact with Ms. Johnson via a contact/fixer of some sort. She'll arrange to meet in person in a very ritzy area, probably far more classy than most 'runner groups are used to seeing. Play up the better-than-thou aspects of the meeting place. Johnson's dressed head to toe in immaculately clean garments, though they lack flair. In terms of design, they're about one step above Flats. She's also wearing sterile gloves. She has the Pathogenic Defense and Tracheal Filter bioware mods, though only the most perceptive or paranoid 'runners will probably find a way to scan for such things. They are a symptom of her growing bacteriophobia. Other than that, her stats can be represented roughly by the Humanis Lieutenant blurb on page 275 of the 4e book, minus pistol skill.

She's all business, and will not shake hands or make body contact with the group unless the situation gets tense. She will be terse and hide her emotions behind a facade of nobility, especially with metahumans. Though she will deal with metahuman 'runners, it's a necessary evil she feels somewhat sickened about.

\synopsis  Ms. Johnson gets right down to the heart of the matter. Barely containing her contempt, she tells them that she needs someone to break into a notorious ork bar, known as the Dunk Tank (this week). Locals call it the Drunk Tank, amongst other colourful names. Since the bar's business hours are shall we say less than cast in concrete, getting in and out while they're closed might pose a problem.

The bar's new name derives from a large (and durable, it's an ork bar) saltwater tank which is its centrepiece. The tank contains a living Merrow, thankfully one that doesn't seem to have developed into a mage. The Johnson willingly admits that her sympathies lie with Humanis in a lot of cases. The ork bar is bad enough, but them bringing in an honest-to-God monster steps over the line. She'll play up all the negative stereotypes one might associate with such an establishment.

The 'runners are to ``deal'' with the merrow. Johnson doesn't specify that this is a wetwork job, but makes it clear that she wants the merrow out of the picture. She's certain that if the bar doesn't have its mascot, it will go belly up soon enough. She's willing to pay whatever the GM feels appropriate.

\notes  This offer should put the group on the fence. Money's good to great, but they'd clearly be working with a Humanis sympathizer. On the other hand, the ork bar really is a rough joint, and they're keeping a sentient being ``captive'' in the tank. Then there's the question of what to do with the merrow. They can kill it, but again they're helping Humanis to thin out the metahuman ranks. If they steal it and release it into the sea, they're letting a monster loose. All of this will be up to the group to decide.

Possible twists involve the merrow contacting the 'runners before they do anything drastic, as it really is sentient and of course doesn't want to die. It's happy enough in the tank, for it's fed and sees a lot of interesting stuff in the bar. By the same token though, it wouldn't mind getting back to sea. Another twist could be subsequent razing of the bar in secret by the Humanis group, who link it all back to the 'runners.

Interesting setting elements to hit on might be the bar itself (bar brawl with orkies, whoo), the salt water tank (especially if someone gets thrown in there with the merrow), and the logistics of kidnapping the monster if they decide to go that route. 

\end{scenario}
