\begin{scenario}{Europa and the Pirate Twins}
	{Investigation; Social}
	{Bought her singles and saw all her films, but that's not quite the same --- it isn't, is it?}
	{GregPogorzelski}
	{2007-04-16}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7177053\#post7177053}

\johnson{Johnson}{Media}  
A very influencial mediacorp executive. He manages the career of a young mediastar.

\synopsis Some creepy Ork guy is stalking a young mediastar called Europa. He's been spotted by Europa's bodyguards at a meeting in Heathrow Airport, London, but it seems he's connected to several incident all around the globe, following the girl from event to event for several months now. The Johnson wants the Runners to actively seek and remove the threat.

\twist Of course, there's a catch: the Mediastar was once a shadowrunner, working with the Ork as a team known as the ``Pirate Twins''---she was the face and the muscle, he was the tech-savvy guy. She went into the shadows as an act of defiance towards her father, a corporate negociator. The father discovered her daughter's hobby and had her vanished from the shadows and her memory magically washed up. He asked an accointance to mediatise her, hiding her in plain sight with a lot of security. When the Ork saw the ads about her latest threedee, a month or so ago, he decided to try and get her back, not knowing about her ``mental state.''

\notes To kick-start the run, you want to a) play up the ``creepy stalker'' vibe (the Ork hideout is filled with her pictures, films-on-chips and paraphernalia, for example) and b) make it obvious that Europa is a bit ``off'' (forgetful mind, strange non-sequituurs, non-matching details about her past...).

It's an open-ended scenario. The Runners can choose either the money or the street cred. If they side for the corp, they'll have to take the Pirate down (and will be well paid for it), but it won't be easy: he's been in the shadows for quite a time, is tech-savvy, has a lot of contacts, and is full of ressources and surprises. If they root for the underdog, they'll have to go down after their own johnson, exfiltrate the mediastar and find a cure, and will have quite a reputation in media circles, but the Pirate Twins will spread the word in the Shadows (fame, new contacts, favors...). 

\end{scenario}