\begin{scenario}{Eviction Notice}
	{Alternate Dispute Resolution}
	{t for... Time to Leave?}
	{Jans}
	{2010-02-03}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=11637133#post11637133}

\johnson{Johnson}{Corporate}  The corp type, a bit more anonymous than most.

\synopsis The Johnson needs the Runners to get people to move out of a middle-class neighborhood one way or another. The people don't want to leave, family, history, etc. are holding them back from taking the purely monetary ``go-away'' money.

They don't want killings splashed across the front page, and no one is going to be shooting back at you, so the run needs to be done in a more civilized manner. Which means that pretty much everything short of actually shooting people up is a-okay. The PCs are being offered a small flat sum, plus a bonus for every household that moves out of the area.

\notes This one is a good way to get your PCs out of the ``Shoot first, ask questions later.'' mentality for completing runs. If they're creative, its probably going to be a cake run. If not, it could be pretty aggravating. Good ways for the townspeople to fight back may include calling Lone Star, talking to the people the PCs claim to represent, alerting the media, or even a spot of blackmail.

The SR3 book presents this scenario as a low level run from the other end, with gangers playing the role of the ``evictors'' (violently) and the PCs on the side of the angels stopping The Man from kicking innocent people out of their homes.

Which, if you want to spice things up a bit, is a good way to do so... 

\end{scenario}