\begin{scenario}{Getting in Deep}
	{B\&E; Acquisition}
	{Some places are easier to get into than others… conversely… }
	{Srathnal}
	{2007-04-26}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7220382\#post7220382}

\johnson{Johnson}{Renraku}  Mr. Johnson is an exec from Renraku. He comes off more as a military man in a suit, which is fine, since he is a military man in a suit. They have discovered the location of an Ares R\&D facility and need someone to break in and jack the relevant items researched and developed. 

\synopsis  On the surface this sounds like a fairly easy assignment. ``On the surface...'' but the problem is – the facility is not on the surface... it is located at the bottom of the ocean, one mile off the coast. The team will need wetsuits and re-breathers and probably weapons that work under water. A smart team will invest in jet skis and/or mini-subs. They will have to navigate past external security, but once inside it should be a piece of cake. 

\notes One of the major parts of the Ares facilities defense is its location and the supposed secrecy of the site. There will of course be some water elementals and deep sea mines to deal with, but there is only a very small security force actually inside the facility.

The Twist: The research being done is magical. A portal to the domain of fire is open inside the facility and should the elemental fire lord trapped inside escape, safety protocols have the facility seal off sections and flood the interior. Which could turn out badly for the runners and the computers that haven't hard saved the days research data. However, the data gleaned from the elemental is… nice. Especially for those mages amongst the team…

Oh, sure, it's a hoop-kicker... but the gains (in data and pay) can make it worthwhile. 

\end{scenario}