\begin{scenario}{Help me find my Mojo}
	{Locate; Retrieve}
	{A beautiful statue believed to be from the area of Rome circa 50 to 150 BC has been stolen from a local collector. The collector wants it back but is not willing to go through normal channels.}
	{Wizard\_Thoarin}
	{2012-08-30}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=15839760\#post15839760}

\johnson{Johnson}{Any underground for security type} 
 Mr. Johnson may be a Fixer, Mr. Johnson, Mafia Don or any person or organization with ties to the criminal world. Mr. Johnson may also be a member of a security firm that was contracted for protection of the owner's property and or person.

\synopsis
 Mr. Johnson hires the players to retrieve a rare and beautiful statue recently stolen. The players are given a 3D holographic scan and description of the item. The item was stolen from a penthouse in a high class building with AAA security. The players are given a single security badge that will allow a single member of the team to enter the building and residence where the item was stolen from and that player may search the premises (this person is accompanied by two of the buildings security guards at all times except if the PC needs to use the bathroom). Note: the players may trade off use of the badge allowing all players access to the apartment but only one at a time.

At the penthouse apartment the players may make rolls to determine the following information:

\begin{itemize}
\item    entry point of the criminals.
\item    exit point of the statue.
\item    exit point of the criminals.
\item    apartment security has been successfully hacked and wiped.
\item    building security has also been successfully compromised and wiped.
\item    other security in the area was also hacked including any security drones in the area of the apartment.
\item    one security drone in the area has a hacked hidden backup area of memory containing a copy of all information that was erased by the unauthorized hacker including video of a black unmarked helicopter in the area the night of the robbery with a clear picture of the pilot as well as the icon(s) programs and procedures used by the unauthorized hacker of this single drone.
\item    spike in magical background count +2 above normal.
\item    powerful area sleep spell maintained cause the spike in the background count and affected the apartments above and on either side of the robbed apartment.
\item    signature of magician that caused the spike in the background count.
\end{itemize}


Much of the information listed above is given out only on a success test to be determined by the GM. The more successes the more information of course. The GM should determine the threshold for each type of test.

The players use whatever information they were able to gleam from the apartment to track down the culprits, a medium sized corporation with offices in the area of operation. The players will have to enter and search several possible locations for the statue which includes:

\begin{itemize}
\item    Corporate Offices
\item    Two warehouses
\item    Airport hanger
\item    Cargo ship at the docks (if the city is sea side)
\item    Apartment building used for middle and upper management at the local corporate offices
\end{itemize}


The item is actually located on the top floor of the Corporate Offices behind a magical barrier as a team of magicians prepare to use the statue in some nasty ritual magic that will turn a rival companies executives to stone.

The players must then gain entry onto the top floor of the Corporate Offices and into the large conference room where the ritual magic is being performed. Corporate Security must be bypassed or neutralized. The item must be retrieved (note if the ritual is completed the statue changes from a beautiful woman to a hideously frightful Medusa statue whose eyes can turn you to stone if looked into).

\notes
 Pay should be determined by the condition of the statue upon retrieval:

If the ritual was interrupted and the statue is retrieved as it was when stolen is worth 1d6 million credits on the art world and 1d6 million more as a magical artifact. If the players learn this they may renegotiate their contract from 2\% of the art value of the item to 5\% of the full value. If the players try to fence the item on the black market they quickly get a final offer for 10\% of the items value but must live with the consequences of their actions (breaking a contract with the client and a hit put out on the players by the original contractor).

If the statue is retrieved after the ritual is completed Mr. Johnson doesn't pay anything because its not the same statue and thinks the players are trying to pawn off crap on him. Should Mr. Johnson accidentally look into the Medusa statues eyes he is turned to stone (any glitch around the Medusa statue turns the person who glitched into stone) and then he can't pay the players unless they find something to return Mr. Johnson to his natural form which would be a different run.

\end{scenario}