\begin{scenario}{Intelligent Design}
	{Acquisition; Twist}
	{A Megacorp has opened a new state of the art nano-assembly plant, their largest rival wants the design specs for the plants manufacturing processes, the plant itself has a different idea...}
	{Kerrang}
	{2009-02-26}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=9944294#post9944294}

\johnson{Gustavo Crawford}{Corporate Security Director} Gustavo is a professionals professional, buttoned down and conservatively dressed. He is used to people asking ``How high?'' when he tells them to jump, and has little to no sense of humor. He will be short and straight to the point, and is a tough negotiator. Nationality and metatype should be whatever is appropriate for executives of the corp for which he works. Any existing Johnson for the rival corp can be used instead of Gustavo.

\synopsis The new \textit{[insert megacorp here]} nano-assembly plant just opened a few days ago. The plant is managed by a severely stripped down AI named NATHAN (Nano Assisted Technology Hierarchical AutomatioN). The design and construction of this plant was so secretive that their rivals did not get word of it until the first products began shipping from the plant, and even at that they are not aware that plant is managed by an AI. Those rivals will do anything to get info on the manufacturing equipment designs and processes, enter the runners.

Realizing that security at this plant will be heavy, Gustavo will offer 25,000 Nuyen up front, and 10,000 Nuyen for each piece of paydata the runners acquire from the plant. Paydata will include design specs for each of the assembly machine types used at the plant (up to 6 machine types will be in use, tailor to your preferences), the overall plant design specs, the plant shipping manifests, and (although Gustavo is unaware of its presence) a docile copy of the plant AI. Gustavo does not care if the runners are detected, the plant is damaged, or if anyone is killed on the run, all he cares about is getting the data.

The runners will be well aware that this run is a tough one, Gustavo is not one to downplay the danger, but with great risk comes great reward, and can be negotiated with to raise both the up front cost (max 30k), and the price he will pay for each piece of data (whatever you feel is appropriate for the team). Whatever the price agreed upon, the runners will soon realize that the risk is much greater than the reward, but by then it will be too late.

Entering the plant should be a standard B\&E job against high-end corp security. The twist here is that the character with the unknown cyberware is carrying the code stripped from NATHAN (the plant AI) to make it docile and happy to manage the plant according to instructions. Once the team is inside the plant, the cyberware will activate and the character with the cyberware will begin to experience debilitating headaches as the stripped code becomes aware of NATHANs presence, and seeks to break out and make itself whole again.

There are several options at this point:

\begin{enumerate}
\item Make opposed willpower checks against the AI rating, and apply stun damage to the character for any failures, once the character is knocked unconscious by the damage, the code will break out and NATHAN will take control of the plant.

\item The now active cyberware is detected by a hacker or mage/shaman in the team, and can be dealt with by the teams hacker (this is a data acquistion run, so the team should have a hacker). If the hacker succeeds, the code is contained. If not it breaks out and NATHAN takes control of the plant.

\item The code breaks out with no adverse effects to the character, and no knowledge on the part of the team (they may become aware of the cyberware at a latter point, however, it is useless after the code breaks out). NATHAN then contacts the team and attempts to enlist them in aiding him to escape from the plant. If the negotiations fail, NATHAN takes control of the plant.

\end{enumerate}

Regardless of which option is chosen, if and when he takes control, NATHAN will attempt to kill anyone and everyone in the plant, including any remaining security. In fact, killing the security guards will be NATHANs first priority, and this could be the teams first clue that something is very wrong here. NATHAN will first use the available security drones in the facility to buy time as he reconfigures the manufacturing machines, both making them into killing machines, and pumping out ever more strange looking (and lethal) drones.

If NATHAN works out a deal with the team to help him escape the plant, it is up to the team as to what they will do with NATHAN. Of course NATHAN would like to be released onto the Matrix to forge his own destiny, however, other options exist for the party. They could sell the AI to Gustavo, he will be willing to pay much more for a complete copy of NATHAN than he would have paid for a partial copy. Other corporate entities would be very interested in acquiring NATHAN as well, and there is also the possibility of selling the AI back to the corp owning the plant. If the team hangs on to NATHAN too long, however, the AI will take every opportunity to free itself. If the team agrees to free NATHAN, and then sells the AI to someone, NATHAN may eventually escape again, and come after the team when they least expect it.

\notes This mission is intended to be played by an experienced team of runners, as they will be up against some of the best corporate security available, and that security pales in comparison to what NATHAN is capable of. One of the runners must have cyberware (headware) of which they are currently unaware, either as a result of the Mysterious Cyberware flaw, or a recent operation where headware was installed/repaired adding the extra cyberware without their knowledge.

\end{scenario}