\begin{scenario}{Internal Competition}
	{B\&E; Sabotage}
	{You can get a promotion by doing better than your peers, or making them do worse.}
	{Alan De Smet}
	{2017-02-19}
	{}

\johnson{Boyd Ward}{Any megacorporation} Ward is Director of Cyberware Research inside of Research and Development.  While relatively high up the corporate ladder, he's nervous; the corporation has specialists for negotiating less-than-legal contracts, but for obvious reasons he cannot make use of them.

\synopsis Like any large organization, corporations are a mess of squabbling fiefdoms, fighting over budget allocations.  Of late, biotechnology, especially bioware, has been a shining light, and Director of Bioware Research Spencer Munoz has seen his budget growing. Rumors suggest Munoz is next in line to be promoted to VP of Research and Development.

Ward has been badmouthing the bioware team's work for the last month, so he thinks he's in a good position to look prescient, so long as a new piece of bioware fails catastrophically soon.  That's where the runners come in.  The runners need to sabotage a piece of prototype bioware that will be exhibited to executives soon.  The bioware needs to fail spectacularly; death of the wearer is a good option.  The failure needs to look like an accident or mistake; it cannot look like intentional sabotage.

The pay is okay, but unexceptional; it's coming out of Ward's pocket.  On the up side, Ward will give the runners almost any information he can. All of the research teams are strongly isolated to limit the danger from corporate espionage, but Ward can still provide accurate, up-to-date information on security procedures, estimated forces based on budgets, and similar information.  Ward will not provide any direct access or identification; there is too much risk that they might be traced to him.

\notes Given how noisy runners typically are, this may be something to conceal inside of a theft.

Security at the research facility will be high.  It's possible that some of the security is using prototype bioware and will present unusually dangerous threats.  

\end{scenario}
