\begin{scenario}{It's Three In The Morning...}
	{Locate; Retrieve}
	{...and a kid's wandering the streets being hunted by the Azzies for what they put in her head. Just one snag: whatever it is, it makes her impossible to find magically.}
	{Phantom Stranger}
	{2007-10-04}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7895710#post7895710}

\johnson{None}{None}  None. Shadowlands is buzzing with the news, and it's clear the kid'll be safer in the hands of another meg. They'll probably pay well to get hold of her too---but you'll have to do the negotiating yourselves, gang. Or your fixer will.

\synopsis A run down into Southern Cali went bad. One lone runner survives from the team that extracted the poor girl, and he can't make the handoff to the Johnson he used---that Johnson is dead, and left no clues to the corp he worked for. She's hiding out in your city while Azzie forces and hired guns (other runners) tear the streets up looking for her. Trace her, find her, talk her down or take her out of the picture---but try not to terrify the little girl.

\notes 
I ran this set in the 2050s and hinted heavily that the girl was a manufactured forerunner to the otakin, though that's not necessary to the story. Wherever the team manage to hide her, they may well end up being hired to run down to Cali themselves to grab some items she needs (tailored food for biotech implants?). Making the surviving runner a former friend to a PC works pretty well.

\end{scenario}