\begin{scenario}{A Kiss Before Dying}
	{Infiltration; Wetwork}
	{You've already got the kidnap victim. Now you just need to get him to his dad...}
	{AbusePuppy}
	{2007-10-04}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7898113#post7898113}

\johnson{Triple-D}{Independant or Syndicate Fixer} A tall, elderly gentleman, proud in demeanor and impeccable in dress. He is very professional and expects to be treated the same. He's been working in the shadows for decades now and knows all the tricks, but will treat a newer team well if they seem promising.

\synopsis The fixer hires the team to do a reverse extraction- he wants them to sneak into a private residence with a young child in tow- concious or not, depending on how hard you want to make it- and make contact with the owner. Let him talk to the kid, who was recently kidnapped as a threat against him, and have his tearful reunion... and them kill the child in front of him. He pays rather well, even for wetwork, since it's a pretty nasty job no matter how you look at it.

\notes The man backed out of a deal with your employer and even threatening his family wasn't enough to coerce him into doing it, so he wants the kid killed as a message to him. (What \textit{would} make a man that desperate not to cooperate?) Triple-D should seem unhappy that he has to do this, but not regretful. In my game he had the runners call him right before doing the killing so he could speak with the man beforehand; this raises the tension a bit, as it's harder for the team to back out. I also didn't have Triple-D initially tell them they were going to kill the kid; it's a good way to put their morals against their wallets. 

\end{scenario}