\begin{scenario}{Large Item Retrieval}
	{Heist; Retrieval}
	{A simple retrieval operation from a low security warehouse. Only problem: the package is the size of a car.}
	{Alan De~Smet}
	{2017-01-16}
	{}

\johnson{Johnson}{Corporate} The Johnson is no one special; just another corporate suit.  They've got a simple job: steal something from another corporation while it's temporarily staged at a low security warehouse.  As is usual, the package is not to be damaged.  One small detail: the package is a crate the size of a car.

\synopsis  The package's current owner is Ares, or your favorite corporation of the moment.  It normally would have been in high security corporate storage, but circumstances meant they needed to move it for a few days. They need to do repairs after the last set of runners stormed through.

The employee charged with moving everything out has no idea what's in the crate, only that it can't be allowed to get too warm. So as a cost saving measure, they decided to ship it out to Silva Refrigerated Storage Solutions, a low security, third party warehouse.  No one would know it was there, and the savings might end up in their yearly bonus!

Unfortunately for the Ares employee, someone else did find out, and sees an opportunity.


\notes  Security at Silva is light. Ten-foot chain-link fence with razorwire, mostly to discourage vandals.  In theory anyone dropping off or picking up a package is checked multiple times, but the Silva guards never see real trouble and let in anyone presenting plausible credentials.  The Silva guards aren't up for real trouble; an exciting week for them is dealing with a malfunctioning automated forklift. If things get violent, they're out.

The building itself is a big box, primarily a single, large, cold room full of shelves and crates. There is a loading dock, a small security station, an office, and restrooms.

That the parking lot is unusually full may be a clue that there will more than the usual number of guards.
Ares isn't entirely foolish, and have sent along additional guards and a mage to keep an eye on things.  Some of the guards may have combat cyberware.  The guards are professionals and view the Silva staff with disdain. Unfortunately, this means they don't actually know the Silva staff, and might not notice if they were replaced.  The mage is bored out of their mind and is holed up in the security office ``keeping an eye on the cameras'' but actually playing video games.

The nature of the McGuffin isn't important. It might be a self-powered cryogenic system holding a dragon egg.  The important part is that it's irritatingly large.  It won't fit in anything smaller than a delivery truck, and it won't fit on anything smaller than a flatbed tow truck.


\end{scenario}
