\begin{scenario}{Last Will}
	{Delivery; Wetwork}
	{Drone pets don't induce allergies}
	{Omen David Derry}
	{2012-08-28}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=15834341#post15834341}

\johnson{Johnson}{Wealthy Family}  A young man or woman in their early-mid 20's. Most likely human, (s)he is rather heartless, but good at hiding it.

\synopsis The Johnson wants you to deliver a Drone pet (if you need to give it stats, use the Bust-a-Move drone from (\fmttitle{Arsenal} p.117) to his/her decrepit old grandmother who is in a nursing home. The Drone pet is a minidrone shaped like a cat, and covered in fake fur. The Johnson tells you that ``This cat looks just like granny's pet cat that she had to give up when she developed asthma. You see, she's always been allergic to cats, but just dealt with it out of love for her pets... At least until she developed asthma and had to give up her cat just to stay alive.'' Along with the toy drone pet, you are given delivery uniforms, directions to the nursing home (along with a floorplan with ``granny's room'' circled in red), Flowers, and a ``Thinking of You'' card. You are instructed to not bring weapons into the building, you may bring weapons, just leave them in the vehicle. You will also be granted use of a delivery vehicle.

\notes 
    The ``cat'' is rigged with a toxin sprayer loaded with Breathtaker (\fmttitle{Arsenal} p.83) or the toxin of GM's choice (either way, Granny's gonna kick the bucket). The security at the nursing home has no reason to suspect anything foul from the runners if they don't bring weapons into the building, even if they see them place an assault rifle in the delivery truck, after all, the nursing home is not in a great neighborhood. If the team does any research on their Johnson, they shouldn't have much trouble finding out that (s)he is one of only two in a wealthy family, the other relative is the grandmother. If the team digs deeper, they'll uncover more hints about the ultimate motive of the run, such as a Will and/or Life-Insurance Policy. If you have a team of runners that have no qualms killing the elderly, you can let them in on the details, or even have them devise their own way of delivering a discreet assassination, so long as it's not too obvious so it doesn't raise suspicion. This run was made to suit a party with a member who goes out of their way to protect the defenseless (the whole party tries to avoid killing children, but only one said \textit{no} to killing off granny). 


\end{scenario}