\begin{scenario}{Lights, Camera...}
	{Debt Collection}
	{TODO}
	{DeeCee}
	{2007-04-15}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7173581\#post7173581}

\johnson{Johnson}{Independent Business}  Mr. Johnson's looking for some hard cases. A local BTL and simsense provider has had a few folks skip out on their outstanding debts lately, and he wants to make an example out of one of them.

The Johnson runs a small simsense studio, one which caters to both the seedier, greasier side of simsense life, and allegedly provides the more-addictive programs which have the moderation filters removed.

\synopsis  The money couldn't be easier. It's not a high-paying gig, but all the 'runners need to do is track down the debt skip and make him regret his actions. The Johnson is quite specific in the manner in which such regret is to be inspired.

The mark should be easy to find: he's a huge troll to whom goblinization was not kind. He doesn't try to hide his looks, and in fact has nanotattoo work covering most of his body which causes his skin to flash with animated corp ads. Anything to pay for that next simsense ride.

Johnson provides four Fichetti Pain Inducer guns, and wants the 'runners to go to town with them. He's well aware that the mark won't be able to pay his debt, so he expects to get his money's worth by having the group assault the mark where enough people can see it so that word gets around. The more pain they give the troll, the longer it lasts, the more money they'll get.

\notes  The real story is that the troll is indeed in debt to the simsense provider – but he has found a way to pay that debt independently. The troll is working with the Johnson. He has agreed to undergo a savage attack in public, but his simsense rig will be recording all the while. He's even agreed to take emotion enhancing drugs to make the whole thing really ``pop.'' For this, his debt to the simsense pusher will be wiped clean.

And what does the pusher get in return? Well, he gets the proverbial glass full of liquid pain in the form of the simsense recording. He intends to remove the safety limitations on the recording and offer it to his seedier contacts in the business. Masochists will pay for such a terror, but he expects to make most of his money from people who want to torture simsense-rigged victims.

Complications: Aside from the moral question, there's also the fact that nobody, not even a hard-as-a-coffin-nail troll burnout, takes a four-Fichetti assault lying down. The troll's going to flip out, and that's bad news to the 'runners. This scenario can also be used to bite your group in the behind, if you're trying to curb in their more antisocial tendencies. If they really get into the attack, the simsense recording is going to be truly terrible. Then they'll have to deal with that recording being used in crimes down the road, or possibly used on them if they run afoul of the wrong circles. 

\end{scenario}