\begin{scenario}{The Little Girl}
	{Mystery; Rescue}
	{Rescue a neotenous girl from a clandestine lab \emph{quickly}.}
	{Omen David Derry}
	{2012-08-30}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=15841535\#post15841535}

 I used this as an opening to a campaign, and the team pulled it off before sunrise.

\johnson{Jason Hedrick}{Cook and Best friends with the Bartender} 

\synopsis  There's allot of red herrings you can throw at the PC's in this one if you really want to give them the runabout. At the bar, the surveillance systems include the alleyway, but it doesn't show the kidnapper (not at first anyway) 1. If the team searches the alley for clues, they might find a syringe that, if tested, they discover was loaded with knockout drugs and used on the kidnapped girl 2. Considering that the kidnapper wasn't seen in the surveillance camera, the party might try magical forensics to attempt to locate the caster by their astral signature (if they don't waste too much time that is) 1. If they still don't have any clues after an hour, you can throw them an image of the kidnapper that appears in surveillance where it hadn't before 1. Eventually they'll find the kidnapper in an abandoned building across the street from a hospital. Upon display (or use) of force the guy quickly gives up info on who paid him... Doctor Gregger 3. If pressed for more info, he'll also tell them that he dropped the kid into the back seat of the doctor's car. The hospital across from the abandoned building is run by Monobe. If the team asks around in the hospital about Dr. Gregger, one of the receptionists mentions something about him having a private office somewhere, though they don't have any idea where it is 4. One way or another, you can feed them clues to the whereabouts of his private office. When they eventually find it, it turns out to be on the 3rd floor of an abandoned apartment building. There isn't an elevator, just a stairwell, halls and doors to empty apartments. There's some cheap old-school security systems in place in the stairway and halls that only warn the people inside of the presence of the runners, there won't be any police involvement. When they get to the apartment that's being used as the doctor's private office, they find a wooden door that's locked with an old style mechanical lock. When the get through the door (either by picking the lock or bashing down the door) they'll find that the doctor has a small security force in the living room (set up as a makeshift waiting room). After dealing with the security, the team finds the bedroom door (not a cheap wooden door like the main door) locked from the inside, and as they go to try to open it, it opens on it's own. What the party sees when it opens? Why it's the kidnapped girl holding a sharp object to the ribcage of Doctor Gregger 5. As she sees the dead security guards and the team of runners, the knockout drugs from earlier kick back in, and she passes out again leaving the doctor staring down the barrel of a gun in the hands of a runner. If the runners inspect the bedroom, they'll notice it's been converted into a lab, there's a dead body in a labcoat on the floor in a large pool of blood with only one wound (inner thigh - femoral artery puncture). As the team goes to leave they get a call from Monobe, apparently the corp caught wind of what's happened, and offers to pay the runners some hush money (and keep the cops out of this) if they destroy the lab and kill Dr. Gregger.

\notes When I ran this one, I had one of the PC's (neotenous hacker/rigger) get kidnapped instead (being genetically unique can have unexpected drawbacks)... to be fair though, I privately talked to the player about it first and they thought it was a fun idea, so we went with it.

\begin{enumerate}

\item The kidnapper paid a nearby street mage (or shaman) to cast invisibility on them, and sustain it for about 1 hour. If they track down the caster, he'll tell them who paid him for 100 nuyen ( if they tell him about the kidnapping).

\item The syringe has no prints on it, but traces of the kidnapped girl's blood can be found, and the drug inside can be identified as narcoject.

\item Data Searches on Dr. Gregger show that he worked for Monobe as a prenatal genetic engineer. A good search result will tell them that his employment was terminated for performing illegal research (if the search result was exceptional, they'll find out what the research was). The research he was performing was related to his work, prenatal genetic engineering (commonly known as "designer babies"), and trying to provide select customers with neoteny as an option (which was prohibited by the corporate courts due to the social and employment disadvantages this poses to the child later in life).

\item If someone in the team has one of the following contacts: Street Doc, Squatter/Gang Member/Gang Boss (in the redmond/equivalent area), Police Officer (any rank) : they have a 25% chance of knowing that it's somewhere in [the redmond barrens or equivalent area in your campaign], if they know that much, there's a further 25% chance they know which "neighborhood" it's in (within a 5 block radius), at which point they can search for his car.

\item Behind the scenes: The girl has cybereyes with (among other things) a tool laser. Dr. Gregger put her in a cage, from which she cut a bar (fabricating a makeshift stabbing device) and cut the lock. During the raucous in the "waiting room", she stabbed the doctor's assistant in the femoral artery and held the doctor at point, forcing him to open the door.

\end{enumerate}

Reward: The team gets whatever hush money Monobe offers, possibly some assorted gear from the security team the Doc hired, they might even try to steal the doc's car if they're exceptionally greedy. If the bartender was already a contact, the loyalty rating goes up by 2, if not, then they gain the bartender as a contact with loyalty 3. Jason Hedrick is useless as a contact, but his girlfriend (the girl you saved) used to work for ARES before SURGE reversed her body's aging (neoteny), and is an outstanding armorer and mechanic with several contacts in the underworld (she works on cars, guns, and various tech for the gangs and syndicates), her connection rating is 2, her loyalty is 4. 

\end{scenario}
