\begin{scenario}{My Daughter's Keeper}
	{Retrieval}
	{Bring a runaway daughter home to her father. Sounds simple, neh?}
	{Bull}
	{2009-05-08}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=10333900\#post10333900}

\johnson{Darrick Erding}{Father}  Darrick hires the runners to bring his daughter Samantha back to him, safe and sound. A Matrix search turns up that Darrick is a successful businessman who isn't aligned with any particular Megacorp, but does business with all of them. He was also given an item in Dunklezahn's Will: ``To Darrick Erding, I leave the Banner of the Red Dragon out of respect for his heritage.'' He seems sincere, and has a clean business record, and comes across as very open and honest, if a bit desperate to have his daughter found and returned.

\synopsis  It's a simple run, find and retrieve a runaway rich girl who's slumming it with some gangers and thinks she's ``in love'' with a lieutenant in the Rusted Stilleto's. But as the runner's start looking, the city begins erupting into a violent war between several of the cities major gangs. The violence starts small, but eventually begins to engulf the entire city, eventually leading to the mayor to declare martial law and bring in the military for support.

Chasing leads leads the PCs into the middle of several conflicts, and eventually they end up in the middle of a three way brawl between the Ancients, the Stillettos, and a 3rd random gang. The bullets are flying fast and furious, and anyone not wearing the right gang colors is a target. And while Shadowrunners are big and bad, even they need to duck and cover when there's over 3 dozen armed assailants, all willing to take shots at them.

\notes Darrick Erding isn't just a father looking for his daughter, he's also a dragon. So is his daughter, who is the dragon equivalent of a teenager, and rebelling in typical teenage fashion. She really is in love with the ganger, though whether he feels the same way or not is up for question. He doesn't know about her true nature. If he gets hurt during the fight, she'll lose control, reverting to dragon form and lashing out at anyone who gets in her way.

This adventure actually takes place during events from the old FASA module ``Elven Fire,'' which involves Shadowrunners trying to stop a gangwar between the Ancients and the Stillettos. This adventure assumes that this Runner team fails it's mission, and the city begins descending into flames, with the PCs caught in the crossfire.

If the PCs are sympathetic, or willing to work with Samantha and her boyfriend, the end fight can be pretty easy. She can keep her identity under wraps and pretend she's a mage, using some minor magical abilities to help out. Or if her cover is blown, she may just go all scaly and help out. But if the PCs try to take her by force, or harm her boy, they'll have to find a way to subdue her without hurting her.

\end{scenario}