\begin{scenario}{Open Sorce}
	{Reconnaissance; Intimidation}
	{TODO}
	{DeeCee}
	{2007-04-16}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7175542#post7175542}

\johnson{Johnson}{Hermetic Mage} 
The group is contacted by a slick corporate wage mage, a woman in her mid-50s with several designer foci about her person. To those in the know, she is instantly recognizable as being of the Hermetic Tradition.

\synopsis Said Johnson tells the shadowrunners of her ongoing project, sort of a SETI@home ritual spell. She operates a network of hermetic contacts who are all working on an enormously powerful and longterm Ritual. No one mage is completely responsible for the full Ritual; they all periodically deal with what a decker might call subroutines of the Ritual, adding miniscule amounts of power to the gestalt.

The problem is that once local shamans heard about what the Hermetics might achieve without the need for a ghost dance, they began to counterspell and sabotage. They were initially only a nuisance, but now their efforts threaten to derail the entire project. The PCs are being contracted to locate the shamans and put a stop to this monkeywrenching.

\notes The Hermetic Ritual takes advantage of the logical and process-oriented roots of their tradition. Hermetic mages involved with the project undergo a screening process and magical testing, to be sure that they can handle the workload. After that, they are taught a few spells which link them to the overall gestalt, and assign them tasks or maintenance duties accordingly. A lot of this is either research or refinement work, and often involves sustained spells. Since the Ritual only makes use of the best results of any particular task which has been outsourced to the cabal, successes are accumulating rapidly.

The Ritual itself is designed with several steps, all with hundreds of subroutines, in the best complex and anal Hermetic style. Overall though, it breaks down into three steps:

\begin{enumerate}
\item Calculate, explore, map, and contribute data about the astral pathways needed for the overall result. This step has mostly been completed.
\item Establish contact with a superior spiritual force, in order to channel the vast energies of the Ritual's conclusion. Summonings play a huge part here, with the gestalt project always needing Spotters for subroutines.
\item Link the inner circle of Hermetics and invoke the endgame of the Ritual.
\end{enumerate}

The superior spiritual force the Hermetics will eventually contact is associated with the planet Mercury. The end result of the Ritual, what the cabal are hoping to achieve, relies on the sheer complexity of the thing to remain secret. In order to figure it out, an investigator would have to become a contributor and perform several subroutines at exceptional ability to understand the greater working.

The enemy of the Hermetics is actually only one shaman, but he's backed by Native support. He's a snake shaman using disguise and subterfuge to counterspell the project, which he and his backers feel oversteps the bounds of common sense, and would give the non-spiritual magic world far too much sway. If the Hermetics can achieve what amounts to a Great Ghost Dance with little individual strain on their mages, it could mean dominance.

GMs might run this scenario simply as one in which the 'runners track down the snake shaman and make him stop his efforts, or they might tie it into a larger campaign which involves a lot of Hermetic magic and finding out what the end result of the great Ritual will be. PC shadowrunners might even work their way into the Ritual itself, provided they have the chops. In such a case they'd be contacted almost daily with various and sundry tasks to attend to involving casting spells, summoning spotters, or simple research. It's a good way to make use of non-combat spellcasting. 

\end{scenario}