\begin{scenario}{Opposites Attract}
	{Survival; Investigation; Retribution?}
	{A case of mistaken identity (you hope).}
	{Reaganstorme}
	{2009-05-08}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=10333218#post10333218}

\johnson{Johnson}{Favorite Fixer} The team's favourite \textit{other} fixer, not their regular fixer, but the one that has sent them on the fewest tail-chasers, got them into the wildest parties, or garnered the team their favourite toys, etc, contacts the team with a dire warning ``Corporate hit squad incoming to your location!'' before static cuts her off.

\synopsis Said corporate hit squad crashes in just as the team grabs their weapons. Whilst it would seem that the corps should have the upper hand due to overwhelming surprise, they seem kind of off balance. The corpers target the wrong locations of each runner's weak point; for example they target the Troll with a left cyberarm and with poison and aerosole filters with knockout and tear gas; they target the binder mage with a fire spirit; and so on. Consequently, the corp team, trying to taunt the runners by using their real names (Take that, Paula Giomarti!), fail horribly.

The team can now try to contact their now definitely favourite fixer, but no dice. Some investigation reveals that there is a duplicate runner team that seems eerily similar to themselves (even going so far as to trade on their own names!) but with a few interesting details: The troll has a right cyberarm but is allergic to pollutants; the mage is a great healer, but is afraid of fire; and so on. Can the team find out why they have been set up, and can they rescue their potential saviour?

\notes The team's second choice, but firm favourite, fixer is looking to expand her stable of regulars by recruiting some of the more successful teams away from her rivals. Her choice team, the PC's, haven't really taken her offers as much as she'd like, despite the choice jobs she's gotten them. Trying to recreate that lightning-in-a-bottle essence, she's drawn together a group of individuals under contract that as closely as possible resembles the PCs, going so far as to get each individual to work under assumed names.

As we all know, a team of individuals never performs as well as an individual team, and this has come back to haunt the fixer as they botch job after job. The Corp the fixer has been hitting lately has begun to do some backtracking, and latched onto the wrong team (ie the PCs). Finding out just before she herself is attacked, she manages to get a quick warning out.

\twist This can be played a few ways, such as if the GM decides that the opposites and their botches were all on purpose to put the PC team in her debt, and thus more likely to take work from her, instead of just trying to recreate the team. And what happens if the duplicate team finds out their real purpose and decides to extract their own revenge if the PCs rescue the fixer from the Corp (especially as it seems that they can work together well now that they actually have a common interest - revenge). 

\end{scenario}