\begin{scenario}{Pay for Play}
	{B\&E}
	{Mel Cozi gets what is coming to him.}
	{Kerrang}
	{2009-02-07}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=9948053\#post9948053}

\johnson{Brandeen Mettlinger}{Civilian} Brandeen is the single mother from the Food Fight 4.0 mission, her baby daddy (Mel Cozi) just tried to off her and their son to keep her quiet, and now she is out for revenge.

\synopsis In the Food Fight 4.0 mission, my group saved Brandeen and her kid, and left the surviving members of the hit squad tied up in the stuffer shack for Lone Star to find. The team talked to Brandeen about why the hit squad was after her, and I hooked them into this follow up with the lure of easy money.

Brandeen informs the team that she has been blackmailing Mel, and has all the necessary information to access his bank account, but she has no hacking skills. Even though Mel just tried to have her and her baby killed, she does not want to return the favor, she just wants to ruin his life and his marriage. She will provide the information necessary to hack Mels account and steal his Nuyen, split the money with her, and send compromising pictures of Mel with Brandeen to Mels wife. She estimates that Mel should have at least 100,000 Nuyen in the bank.

Brandeen does not have the info with her, and it is very late, so she exchanges comcode info with the party and agrees to provide the info and pictures the next morning. When Brandeen calls the next morning, she sets up a meet at a sidewalk cafe/bistro downtown at noon. The meet goes down without a hitch, Brandeen provides the team with the Mels account codes, and the lurid photos.

When the team checks the account info Brandeen provided, they will find that Mel closed the account earlier that morning, so much for an easy run. When I ran this, I had the meet go down very quickly, the team did not have time to check the codes before Brandeen left, and were unable to get in touch with her for some time afterwards. This was important, as I wanted there to be enough time for Mels bosses at Alliance Design to find out about the botched hit attempt. A couple of days later, just as the team had accepted another time-sensitive mission, Brandeen gets back in touch with the team, wondering if they have the money.

Since the account has been closed, Brandeen comes up with another plan. Mel and his wife live in an upscale gated community in Renton, Brandeen provides the team with the address and the code to enter the back gate of the community. She knows Mel and his wife will be at a corporate function tonight, and she wants the team to break into his home, hack into his new acount from his home terminal, and spread the pictures throughout the house for Mel and his wife to find when they return.

In the mean time, Alliance Designs has decided Mel is a liability, and they have hired their own hitman to take him down when he returns home that night. There are several ways this mission can play out from here:

\begin{enumerate}

\item The runners, having already accepted another mission, decide to wait before pulling this job. The next morning Mels assassination is all over the news, and the runners missed their chance. Of course Brandeen thinks she was was double crossed, that the runners killed Mel, and made off with all the loot. Can the runners convince Brandeen otherwise? If not, does Brandeen have the ability to get back at the runners?

\item The runners arrive at Mels home just before the hitman, hack the account, plant the pictures, and get out quick. The hitman notices the runners, but the runners do not notice him. He takes pictures of the team leaving the residence, then kills Mel and his wife when they return home, and sets the team up for the deed by sending the pictures to Lone Star. The next morning the runners find out that Mel and his wife were killed after they left, and that they have been framed for the job. Will they blame Brandeen for the setup? Can they find the hitman, and pin the job on him, and Alliance Designs, before Lone Star catches up with them?

\item This is the way it played out with my group. The break in goes smoothly, the pictures are planted, and the account is hacked to the tune of 100,000 nuyen. The team was smart enough to post a lookout at the front door, and the hitman was spotted staking out the house. The team managed to nab the hitman before he could get away, and Mel was not assassinated, rather, he lost his money, his wife divorced him, and Alliance Designs fired him. The team split the cash with Brandeen, and even completed their other mission on time.

\end{enumerate}

\notes This need not necessarily be played as a follow up to Food Fight 4.0, Brandeen could just be a friend of a friend, or she can be replaced by someone the team already knows. 

\end{scenario}
