\begin{scenario}{Pony up the Dough}
	{Sabotage}
	{TODO}
	{DeeCee}
	{2007-04-16}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7175534\#post7175534}

\johnson{Johnson}{Organized Crime} 
Mr. Johnson is the owner of several illegal games of chance, including a dilapidated horse track. The problem is that virtually nobody goes to the track anymore, especially after several doping and bioware scandals ruined the track's reputation.

To add insult to injury, the Yakuza have opened a virtual horsetrack, one which on the surface appears to be completely above board. In the few months that it has been operating, there have been no questions about the legitimacy of any of the races. No tampering has ever been found.

Johnson wants the shadowrunners to wreck that legit reputation. He wants them to either prove that the virtual track is not tamperproof, or to engage in a smear campaign that makes it seem that it is. If they manage to win a lot of nuyen in the process, so much the better.

\synopsis The virtual track remains clean by a combination of factors. First, the virtual horses, unlike real horses, do not exist from race to race. They are generated on the fly, kept in storage buffers just long enough to accept bets, and handicapped/odds set to five decimal places.

Second, the yakuza have hired deckers and expert systems to design the virtual track, and also to maintain its purity.

Lastly, some of the devotees of the track are thrill-seekers who above all else simply wish to have a level playing field when it comes to their vice of choice. The yakuza track offers them a place to practice their gambling skills without worrying about a fixed outcome. These gamblers have day jobs for the most part, and can bring a lot of varied resources to bear if someone is found to be tampering with their playground.

\notes The yakuza really are playing it straight this time. They make enough from residuals and oddsmaking that if they don't get greedy, will provide them with quite a tidy profit. Reputation means a lot on the street. Retribution for tampering, which will damage that reputation, will be severe. 

\end{scenario}