\begin{scenario}{A quick Trip to the Chip Factory}
	{Uncategorized}
	{You got to know when to hold 'em.}
	{painandgreed}
	{2007-05-03}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7250148#post7250148}

\johnson{Street contact of the players}{None} A street contact of a players who either works eratic deals or is always running random deals.

\synopsis  One of the player's contacts contacts the players and asks for a favor. One of his contacts has paid back an old debt by turning over information on a batch of illegal simsynth chips. All he has to do is show up at the legal factory where they are being made under the table by the local manager (who has already been paid), and pick them up. The street contact just wants backup incase something goes wrong because he's never dealt with these people before. The players need to be lightly armed and act the part of delivery men. The contact will have a truck and coveralls. The plan is to show up at the back dock, request the chips, get them and leave. In return, the contact offers to owe the players a favor, but if pressed can give the players some money in the future (as all he has right now are the chips which are worth a good deal of money), or a few boxes of the chips themselves that would be worth much more in street value. When they show up, they will be told by the guy in the loading dock the chips are still printing, after a few minutes wait, the machines will stop, the dock guy will get the chips, hand them over and the deal is done. So long as the players keep their cool, nothing bad happens. 

\notes  This is all about making the players sweat and keep their cool. Perhaps the dock worker will look at them strangly, or say some strange things. The printing machine might stop and start irregually making the characters just stand there for a period of time. Maybe a police vehicle will hit the lights and siren only to speed on by. Lay on the descriptions and give the players hints that things might not be going right, but so long as the players don't whip out the guns and start shooting, nothing happens.

I also used this as a lead in to another senario as while most of the simsynth chips are exactly as presented, one box (which was in the bunch that the players recieved as payment) is actually other information. Information that other people want very badly. The friend of the contact will end up dead. The manager of the plant will end up dead. The contact will get scared, warn the players and go into hiding. Meanwhile, people after the other chips will be searching out the sources of the illegal simsynth chips for the chips they really want. 

\end{scenario}