\begin{scenario}{Rainslicker}
	{Wetwork}
	{TODO}
	{DeeCee}
	{2007-04-16}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7175552#post7175552}

\johnson{Johnson}{Organized Crime} 
The PCs are contacted by a minor crime boss to do some straight-up wetwork. It's a tough target, so payment should be at an appropriate level.

\synopsis The Johnson tells the group of a target which he wishes eliminated. The problem? The guy has extensive chrome and the best Doc Wagon contract that nuyen can buy. They've tried to take him out before, but he's worse than a voodoo cockroach. Right now the filthy bugger is living high on the hog in a prestigious hotel. The boss won't say the reasons why he wants the target erased.

The mark is actually a veteran Shadowrunner, now enjoying semi-retirement. He's got contacts, he's got skills, he's got whatever nastiness the GM wants to give him. He's bloody James Bond. Taking him out will either require a lot of collateral damage, or perfect precision in the assassination plan.

\twist The boss has hired at least two other shadowrun groups to try to take him out at the same time. One is a rigger-heavy crew using milspec drones, the other a smarter group of Faces who will try to manipulate the PCs into taking out the target, then incapacitate them and claim credit and payment from the boss.

\notes Rainslicker is actually the shadowrunning name of the target, who now goes by any number of aliases. Since he's human, and a lot of humans look alike, nobody has ever really caught on to the fact that he's not the first person to use that name. No no. In fact, Rainslicker is a set of specs, used by the REAL Rainslicker (a doc and techboy) to create a shadowrun avatar for himself.

Basically, the Rainslicker persona consists of a set of cyberware parts, a few hardcore Activesofts and Knowledgesofts, and a willing actor. Since the guy who created the persona spends much of his time immersed in the Matrix, he needed a cover for his shadowrun work in the real world. He thinks of the Rainslicker actor(s) as his avatar in the flesh world, and he pays them well to be over-the-top Bond-style characters. Should the actors incur damage, Doc Wagon is there in a flash to patch them up. Should even that hallowed organization fail to get the job done, the man behind the face simply hires another actor, sets him up with the appropriate gear, and the game continues.

Since someone is bound to stumble upon the secret eventually, the real Rainslicker is in town for ``one more job.'' A high-risk sexy venture that will earn him enough cred and nuyen to coast happily into retirement, unless the PCs get in the way. 

\end{scenario}