\begin{scenario}{Sewer Rats}
	{Paracritter Extermination}
	{Going to need a shower after this run.}
	{Omen David Derry}
	{2012-08-30}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=15842674#post15842674}

\johnson{William Smith}{City Official} 
William Smith works for the city's department of sewers and sanitation. The department is trying to run maintenance on various systems under the streets of [the city], but they've run into problems with the devil rats that live there. He wants you to do whatever it takes to eliminate the infestation without causing any damage to the city's underground infrastructure (this means no explosives).

\synopsis
This is a relatively straight-forward run, but if you think it's too easy for your group, you can throw in some a toxic magician (probably with a toxic mentor spirit) and/or a toxic spirit to ramp up the challenge, though several dozen devil rats should pose significant enough of a challenge for most teams.

\notes
Devil Rats can be found on p299 of the Core Book (Anniversary edition). Toxic Spirits can be found on p144-147 of \fmttitle{Street Magic}. Toxic Magical Traditions can be found on p141-142 of \fmttitle{Street Magic}. Recommended Toxic traditions are either Poisoner or Havoc. Recommended toxic mentor spirits are Pestilent Rat, Pollution, or Radiation. Recommended Toxic Spirits are Abomination, Acid, Harrow, Nuclear or Sludge. It's also suggested to have a \textit{minimum} of 4:1 ratio of devil rats to runners, and a ready supply of mundane rats (use Norwegian Rat from \fmttitle{Running Wild}, p93 for stats). You may also use Demon Rats if you desire (found in \fmttitle{Running Wild}, p152-153). It's important to note that other than the mundane rats, all of the potential targets are either immune or resistant to toxins and pathogens (well, if you use one of the suggested toxic mentor spirits that is).

\end{scenario}
