\begin{scenario}{Slow Bandit}
	{Hooding}
	{Can they outrun a Tortoise?}
	{Dee Cee}
	{2007-04-30}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7237758#post7237758}

\johnson{Johnson}{Mitsuhama Computer Technologies}  Virtual meeting only. State-of-the-Art matrix presence, impeccably dressed and oozing megacorp indoctrination. Johnson is male or female at GM's choice, as there is actually a real person behind the avatar. A real wage slaved, brainwashed, pro-megacorp person.

\synopsis  The 'runners are contacted by the aforementioned Johnson, and in one of the rarest instances in the game world, contracted by a megacorp to actually do some ``good.''

Mitsuhama Computer Technologies is looking to install a bleeding-edge network hub in a rundown part of town. Other corporations think it's a fool's game to do so, but Mitsuhama sees it as an opportunity to establish a presence in an area which they feel is ripe for remodelling. They also feel that if they're the only large corporation in the area, they'll be the only employer, they'll control how things are done, they'll run peoples lives – but always for the betterment of the neighbourhood of course.

The problem is that they are being blocked by hackers and sabotaged at every turn. Mitsuhama has invested quite a bit in trying to virtually stamp out the interlopers, but to no avail. Not only are they looking for someone with decking chops to find out why they've been stymied, but they also need support personnel to deal with the hackers in other ways.

The Johnson wants them to infiltrate the hackers, break up the operation, and secure their hold on the virtual territory that so far has been kept out of their grasp.

\notes  The hackers are led by a Raccoon shaman, of all things. She, like her totem spirit, is mighty cunning with her hands. So much so that she will only do her decking via a dinosaur of a computer system. It's what's known as a tortoise rig; no virtual presence, only straight keyboard-and-monitor technology. It is a testament to her decking abilities that even with such technology (albeit backed by Raccoon magic), she has eluded and monkeywrenched Mitsuhama personnel.

In order to accomplish their run, the team will have to show up on the shaman's radar. This means a few initial hacking attempts, some flashy work, etc. The GM should have some fun with it, as should the 'runners. The shaman will use these initial contacts to determine just how much hacking ability the group has. If the 'runners try to get mean or employ black IC, well there are advantages in using a tortoise rig.

As it happens, the shaman has a group of young hackers convinced that the Mitsuhama entry into their territory would be a very bad thing. She plays up the alleged ties to Yakuza as much as possible, and sermonizes about the ``true'' path to hacking greatness through working with one's hands. In order to further her agenda, she's organizing an actual meeting in the flesh world soon, where she will have a linked series of tortoise rigs set up, and where hackers will compete to be the first to accomplish some legendary computational feat or other. Of course, this would be the perfect opportunity for the 'runners to find all of the troublesome hackers in the local area, and maybe hit them with RFID Pepper Punch for good measure.

Naturally, they'll have to prove that they're worthy to be invited to the hackfest first... 

\end{scenario}