\begin{scenario}{Socialised Healthcare}
	{Acquisition}
	{Not everyone can afford medicine. That doesn't mean not everyone needs it.}
	{Phantom Stranger}
	{2007-04-15}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7172198\#post7172198}

\johnson{Doc Dufreyne}{The Street} ``Doc'' Ida Dufreyne runs a back-alley service for the folks in her neighbourhood (just about slum level). In her late twenties, the ork is considered attractive by most of her metatype, but clearly careworn. Any idealism has long been bled out of Ida, and her personality is driven mostly by determination to help 'her community' and bitterness that they're passed up.

\synopsis Ida can't afford to pay corp rates for medical supplies, nor is it likely she'd be allowed to buy if she had the money. Every so often she can scrape together enough money to point a team of sympathetic runners at a shipment through town and pull the trigger, though. Working for Ida you can expect a couple days' notice and the usual route the shipment takes when it's driven through the city, but from there it's up to you. Get the truck stopped and either take over or extract contents, and get them back to Ida without being followed. The corps won't be happy about it, nor will the Lone Star boys, so it's the second part that's tricky.

\notes Ida pays about three K per runner, or six K's medical care on credit if you want to go that way. She's a ready market for new medical primers if you can find 'em. She listens to her community---she'll often pass on news of other low-paying runs to help the locals. Plus, of course, in a month or so she needs another shipment; only this time, they're aware of the risks... 

\end{scenario}