\begin{scenario}{Stepping Stone}
	{Infiltration; Retrieval}
	{There's one hell of a big job being offered. Problem is, everyone else wants in on it as well...}
	{Regis}
	{2007-04-15}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7172198#post7172198}

\johnson{Johnson}{unspecified} The city's most mysterious patron, renowned for offering strange, dangerous and ludicrously well-paid jobs, seemingly without connection, refuses to meet 'runners in person. Instead he communicates via a heavily secured custom-built holographic transmitter that as yet nobody has been able to tap into. The image projected is of a grinning skull, relaying his every word in a neutral, mid-atlantic accent.

\synopsis The word has gone out that the Johnson of Johnsons has something he wants stealing. It's extremely valuable, he's offering an absurd amount of money for it, and more to the point, he wants absolutely zero fatalities throughout the entire mission. Now, most Shadowrunner teams are good at getting a high body count, but not many are good at keeping it down that low. So, he has a test set up, to ensure the maximum possible efficiency of the team that he employs. An abandoned downtown apartment block has been converted into a maximum-security facility, in the penthouse apartment of which is his personal communications unit. The word has of the block's location has gone out at the same time to half a dozen likely 'runner teams; the first one to make it out of the building with the unit gets the job. The problem is this: the entire thing is being constantly monitored. If any member of any team is responsible for anyone dying on this mission, be they Shadowrunner, in-house security or innocent bystander, their chance to take the contract is instantly revoked. Happy hunting!

\notes The building really is maximum security---money is no object for this Johnson, wherever they get it from, and they have the best facilities money can buy at short notice. As this is just a training and selection job, however, all security measures are as non-lethal as the 'runners themselves will have to be. Very powerful, but entirely non-lethal. This would probably be a good Run to have as the beginning of the end for an esperienced party---the one job that will let them retire on their ill-gotten gains. It also offers a nice challenge for any outfit with a habit of going kill-crazy. 

\end{scenario}