\begin{scenario}{Those Who Hunt Thieves}
	{Acquisition; Wetwork}
	{Someone's not playing by the rules...}
	{Jans}
	{2010-02-03}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=11636919#post11636919}

\johnson{Johnson}{Anonymous}
Mr. Johnson (anonymous): The call should come in from whoever has the most influential fixer contact. The Johnson is fairly standard as these things go, but with a presence that screams money. Immaculately tailored and groomed, wearing several thousand nuyen in business clothing, hiring out a private room in the back of the most prestigious nightclub around, and backed by some serious muscle. An old hand in the business, who connects the stupidly rich with people they wouldn't spit on to put out a fire.

\synopsis 
Most problems in the sixth world have a very specific solution, throw money at it. Nuyen can open any door and silence any problem. Those who have it live a life of luxury, those that don't are left for naught. This is the way of the world.

So it should be understandable that people with a great deal of money are finding themselves targeted. Someone out there has the balls to steal from the rich, and the rich are ``fighting back'' so to say. The Johnson wants you to find the thief, or thieves, and get back what was stolen. Then he wants you to put an end to the problem, permanently. If you can do it, the rewards will be outrageous.

\sectionlabel{The Setup} Money solves a lot of problems, yeah, but sometimes there's no replacing skill. A team of Shadowrunners has gotten it into their heads to buck the system and go independent. They're turning on the Johnsons, the Corps, the Politicians and the Stars and taking what they want instead of letting it come to them.

Normally, this sort of problem would sort itself out. The Runners are pissing off a lot of very important people and they still have a lot of money at their disposal. The problem is that they're good, very good. No records, no suspicious activity, no pictures, no leads, nothing. Whoever these guys are, they're making the best CorpSec has to offer look like a bunch of chumps and they're getting away with it.

\twist You're not the only ones out there looking for these guys. Everyone and their grandmother seems to be out there looking for the thieves, largely because the Johnson is paying on completion.

This kind of situation has happened before, but whoever's behind it this time is taking things too far. The People With Money are up in arms, there's blood in water, and if you aren't careful it could easily become open season on all Shadowrunners.

\notes
What the Johnson offers is largely up to the GM. Serious Runner teams have less need for Nuyen than they do discreet parking and high class refitting for that military grade attack helicopter, a get-out-jail-free card or two, maybe even a cushy job in middle management that they can retire on. The Nuyen help, but I'm sure you can find something to make this run even more attractive for your PCs.

The setup seems a bit pretentious from the GM's perspective. Making a group of ridiculously experience NPCs that are running circles around the Corps and Johnsons can easily lead to ``NPC Attachment Syndrome'' or something similar. If you think you can play it straight, go for it. If not, someone (or thing) else could be behind the heists. One way or another your PCs could quickly find themselves dancing the Charlie Foxtrot.

If you \textit{do} decide to go the Elite Runner NPCs route, make sure you give your PCs a taste of what the ``bad guys'' are getting. A power high where they make the rules, and are responsible to no one else. Hopefully things are fairly hectic by that point and your guys feel the pressure to stop the thieves instead of joining them (or not, Viva la Revolution!) but it will certainly put the idea in the back of their head, especially useful if you ever end up running...


\end{scenario}