\begin{scenario}{Those Who Can't...}
	{Acquisition}
	{TODO}
	{Deacon Blues}
	{2007-04-15}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7173863\#post7173863}

\johnson{Johnson}{Corporate} The corporate type. Typical suit from the Special Projects division. Though the target of the run is Ares, the Johnson's employer is never specified. He could be working for Ares himself.

\synopsis An Ares exec has absconded with certain files from the company's internal network. The Johnson won't go into what they are (and, as the runners discover, it's boring financial data), but provides the team with file signatures that'll identify the package. It's on an optical chip, probably at the exec's house.

Finding the chip will be hard enough. Teams with few scruples will probably just bag the exec and roughhouse him until he talks---a tricky bit of a firefight, as he travels to and from the office with a bodyguard and an armed driver. Stealthier teams might break into his house during the day and painstakingly comb the place---tedious but certainly professional.

\twist On the way back from acquiring the chip, the runners' driver gets a call.

``Atop the building at the end of the street,'' the caller says, ``is a man with a missile launcher pointed at your car. He's acquired signal lock and will slag your vehicle if you don't pull over.''

A van full of gunmen pull in behind the runners, hold them up and demand the chip. The PCs may pull some sleight-of-hand switch, providing a blank chip or a dupe (as a GM I'd let them, as it doesn't really derail the rest of the story). If they don't, the gunmen drive off.

That's right: another team of runners was put on the same gig by a different Johnson. They put their ears to the street, found out about the PCs, and decided it'd be easier to just tail them and hijack the goods than to tangle with the Ares exec.

With money on the line and their rep at stake, the PCs will waste no time in tracking these fraggers down and bringing some street justice.

\notes  If you ever wanted to make a point to the PCs about how ``real'' shadowrunners behave, this is the team you make it with. These guys are pros---they work their contacts, they eavesdrop on calls, they hack every database they can, they operate quietly and discreetly. I promise you: the PCs will start tightening up their procedures and watching their back after getting schooled like this. 

\end{scenario}