\begin{scenario}{Unplanned Obsolescence}
	{Rescue; Extraction}
	{Rescue menomic enhancement ``volunteers'' from an abandoned lab.}
	{DeeCee}
	{2007-04-16}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7175559\#post7175559}

\johnson{Johnson}{Matrix}  The Johnson for this run is an information peddler known only through Matrix connection. The meeting will take place in the Matrix, with the local environment favouring stealth and black IC over flash and aggrandizement. The Blogger (page 282, Shadowrun 4e core) template can be used to roughly stat out the Johnson.

\synopsis The Johnson has a plethora of contacts, as one might expect form an information peddler. She leans towards Mapping and GPS recon data acquirement, rather than dirty little secrets. One of her contacts has called in a favour, and she desperately wants to help, but she's stuck researching Tir Tairngire for another job. She's offering premium prices to the PCs if they can help out her contacts in a timely fashion.

Back in the day before perfected bioware, there were... experiments. The more difficult the end result, the more prototypes had to be refined until perfection was reached. In the case of mnemonic enhancement bioware, these ``prototypes'' had names.

Essentially the PCs will be seeking out the Johnson's contacts, who are always together in the Matrix. If they manage to find the group (three to five Matrix presences) and make a good impression, or at least make it known that they're the hired help, they'll be asked to go to a decrepit building in the real world and rescue the contact's mortal bodies, as they have long since stopped being able to fend for themselves in the world of flesh.

When the PCs arrive, they'll find that the contacts' urgency depends on a couple of factors. On one hand, the building in which they're technically squatters is being demolished within hours. On the other hand, it's a haven for ghouls. The contacts are in a self-contained security area in what proves to be the remains of a scientific research factory.

In order to rescue the contacts, the PCs will need to breach security, and thus expose their targets to ghoul predation. That can't be helped, but risk can be minimized.

The trouble is that the contacts' mortal bodies are actually several bulky containers of mnemonic vat tissue, connected to withered geriatric bodies and several redundant life support systems.

\notes The PCs will have a time of it. Not only do they need to locate the physical bodies of the contacts, but they need to stop the ghouls from destroying them when they do. The contacts' Matrix presences are strong, but their conciousness is almost completely in the machine. Simply disconnecting them might sever all ties to the material world. The last problem lies in transporting several vats of what amounts to brains, along with geriatric bodies and necessary life support, to a location where they can be set up safely once more.

A possible twist might be that since mnemonic tissue is used to foster longterm memory, and since the contacts have been immersed in the Matrix for years, they'll have lots of information and files available to them. The corporation that initially created the vat tissue and the prototypes might not take kindly to their dirty laundry leaving the premises. They had hoped that the destruction of the building would wipe the slate clean. Too bad that in the world of the shadows, cleanliness is next to impossible. 

\end{scenario}
