\begin{scenario}{Walk in the Park}
	{Bug Hunt}
	{A local park warden needs some help with vandals. Unfortunately...}
	{Sword Raven}
	{2007-04-15}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7172067#post7172067}

\johnson{Mr. Porter}{City Wildlife Trust} 
A kindly old man who has looked after this inner-city park for a long time. Budgeting changes mean that he no longer has many park rangers to help out with more difficult tasks.

\synopsis Mr. Porter has had reports of vandalism in the local park, the park itself is fairly big, at least a mile square. Of course, it isn't kids... it's insect shamans attempting to construct an inner-city hive for their queen. The park has an ever-growing network of tunnels underneath which means lots of close-quarters bug-hunting for the PCs and they must also find a way to seal off the tunnels for good.

\notes Naturally lethality could be quite high in this scenario (SR4 anyway) so I would personally consider making them fight mostly human mooks before fighting a few bugs and eventually the insect shaman himself BEFORE he can establish the queen in her new hive.

As for reward, the warden is given a budget of 2,000 nuyen for each member of the team who successfully solve the vandalism problem. This isn't a lot but for the difficulty of the task as presented it should be an easy run. Afterwards the warden offers 20,000 nuyen on top of the 2,000 to keep the runners quiet about what they found.

In order to hook the PCs into a low initial reward, I suggest having the park warden a friend of a friend or a direct friend of one of the PCs.

The vandalism reported is occult symbols carved into trees in a tight perimeter around the entrance to the hive.

I would throw in a couple of gangers hanging around the park but these are a red herring and know little to nothing except seeing 'weirdos' late at night. 

\end{scenario}