\begin{scenario}{I got up and went down to the bar... Life went downhill from there}
	{Survival}
	{TODO}
	{Wizard\_Thoarin}
	{2012-08-29}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=15839610#post15839610}

\johnson{None}{None} This Scenario starts after the players get to the bar for a day off after a successful run, no one is here to hire the player characters.

\synopsis  The player characters are enjoying a relaxing day at their favorite bar (sports bar, nude bar, pure drinking bar or whatever the players prefer). Shortly after everyone has arrived in walks ``The Preacher'' (toxic street shaman the GM may pick the religious background of this NPC). The street shaman starts preaching to the heathens in the bar and after a minute or two finishes and then passes around his hat asking for donations to his church (inside the hat is a typical device for transferring credits from one credstick to another with the preachers credstick locked into the device). Most of the locals in the bar know ``The Preacher'' and dutifully slot their credstick and transfer 10 to 20 credits to ``The Preacher''. The first person to pass the hat by him without slotting his credstick and giving ``The Preacher'' some funds causes ``The Preacher'' to say rather loudly... ``Brothers, come forth for we have a disbeliever among us!'' Once ``The Preacher'' says that line in walk 4 Troll Street Samurai and proceed to lay waste to everyone in the bar... can the players survive 4 Troll Street Samurai and a Toxic Shaman?

\notes  If the players survive the battle in the bar they find a key on ``The Preacher'' that unlocks his credstick from the hat he passed around. Roll 2d6+8 (10 to 20 credits) for each NPC that made a payment to ``The Preacher'' and add 5,000 credits to 10,000 credits (based on how generous the GM is feeling) for "The Preacher's" previous preaching engagements during the day. This is all on a certified credstick after all, ``The Preacher'' is SINless. 

\end{scenario}