\begin{scenario}{Where’s the Kaboom?}
	{Structure Hit}
	{There was supposed to be an earth shattering kaboom.}
	{Save vs DM}
	{2007-04-16}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7174787\#post7174787}

\johnson{Johnson}{Humanis League} A well-dressed human businessman in his early twenties, with a twinkle in his eye and a spring in his step. He looks rather green to be a Johnson, but it’s an act – he’s really quite accomplished. He tries to hire a group containing mostly metahumans if at all possible. He treats them like royalty, doing all he can to identify with their plight and trying to act as nice as possible.

\synopsis The job looks to be an easy one – he wants to hire the runners to plant a low grade bomb in a local Humanis headquarters. He gives them a detailed layout of the facility, including guard shifts and all pertinent security information. The hit is supposed to go down late at night, where human casualties will be at their lowest.

The run looks to be simple – there isn’t a lot of security, and the bomb and information provided should make things run like clockwork. Conversely, the reward isn’t all that big, but the Johnson is counting on the runners sympathies to work cheaply. He will give them a nice bonus if they can hack all the data, but it’s purely option and he stressed not to put them in too much danger.

\twist The Johnson is actually a member of the Humanis league himself. The facility he’s sent the runners to is fairly peaceful by Humanis standards, and he hopes to accomplish two goals with one expendable team. He’s hacked the security network of the building, as well as installed hidden cameras, in order to capture the runners working. Once the building blows up, he plans to use the footage to stir up trouble against metahumans, all while trying to raise the ire of the more peaceful Humanis group. Will the runners figure out that they’re being double crossed in time to prevent being caught on camera?

\notes This run works well to instruct newer teams that things are not always what they seem, and that ire against metahumans still runs high in 2070. This can actually jump start an entire arc if the runners are discovered, as they’ll have to lie low and figure out just who really double crossed them.

\end{scenario}