\documentclass[letterpaper,twocolumn,10.5pt]{article}
\usepackage{fontspec} % setmainfont newfontfamily
\usepackage{titlesec} % titleformat
\usepackage{enumitem} % adjust list spacing
\usepackage[top=0.6in, bottom=0.9in, left=0.7in, right=0.7in,xetex]{geometry}


\newenvironment{scenario}[6]
	{
		\section{#1 {\small[#2]}}
		\textit{#3}
		\def\TMPSCENARIO{#4 #5}
	}
	{\small\textit{By \TMPSCENARIO}}
\newcommand{\johnson}[2]{\textbf{Johnson: #1 (#2):}}
\newcommand{\synopsis}{\textbf{Synopsis: }}
\newcommand{\notes}{\textbf{Notes: }}
\newcommand{\twist}{\textbf{The Twist: }}


\begin{document}



All scenarios are from this thread: https://forum.\allowbreak{}rpg.\allowbreak{}net/\allowbreak{}showthread.\allowbreak{}php?\allowbreak{}321504-\allowbreak{}Shadowrun-\allowbreak{}4th-\allowbreak{}101-\allowbreak{}Instant-\allowbreak{}Scenarios

\tableofcontents

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{Bunraku Breakout}
	{B \& E; Extraction}
	{Does the team have what it takes to break into a Yakuza owned Bunraku parlor and spirit away the daughter of a Mafia Don – without getting caught?}
	{Save vs DM}
	{2007-04-15}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7171841#post7171841}

\johnson{Johnson}{Mafia} The Johnson is a well-dressed and heavy-set Italian man in his mid forties, with salt and pepper hair and a strong nose that looks like it’s been broken at least twice. He speaks in a slightly mumbled Italian accent, and looks every inch the Mafioso – because he is. He meets the team in a small Italian restaurant, even going so far as offering to buy them a nice pasta dinner over arrangements.

\synopsis It seems the local Yakuza kidnapped the wrong Mafia Don’s daughter to “work” in a Bunraku parlor. The Mafia Don is pissed at this affront to his family, and wants to make the Yakuza pay without getting involved himself. Using his extensive contacts, the Don has managed to locate the parlor his daughter was taken to, and also knows that she hasn’t yet been lobotomized. He hires the runners to extract his daughter, and any other Bunraku girl they can smuggle out, just to twist the knife a little. The runners are then to release a rather nasty virus that will wipe all of the data on the stored personality chips on the way out, putting the place out of business for good. The runners are provided with a basic layout of the area, a list of likely guards, and the virus – as well as a time limit of 24 hours. Beyond that, and the Don’s daughter is sure to have been lobotomized and put to work. He offers an excellent reward (double your standard reward), plus an additional 2,000 nuyen for every Bunraku girl smuggled out in addition to his daughter.
\notes  This is a time sensitive mission that works well for groups that are good at silent infiltration and speedy planning. A character who is skilled in hacking will be almost mandatory, though clever groups can either hire one for the job or find another way of implanting the virus. Successfully completing this mission might very well piss off the local Yakuza, but will definitely earn the favor of the local Mafia.

\end{scenario}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{All-Star Defence}
	{Bodyguard; Shadowing work}
	{ Sport is a competitive world. The runners are out to ease the competition for their team}
	{Phantom Stranger}
	{2007-04-15}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7171978#post7171978}

\johnson{Davey Rohr}{Seahawks} Davey Rohr, as he likes to be known, is a jovial human of about forty-six years of age; a former linebacker who had a couple years competition before his leg blew out, when he moved on to security. Now, over two decades later, he's back with the team that gave him his big shot, though he keeps the lowest profile he can; he's the executive interface between team, security, and the shadows. Sports is big business and you'd be surprised how many jobs they can't admit to.

\synopsis The Seahawks are looking to make the steal of the year---there's a troll running back coming up out the college leagues who covers ground like an elf. One of their scouts is bringing him in this coming Monday, they're wining and dining him for three days to swing him round. A number of other teams are very interested in preventing Joss Wallach from signing with the team, either to lure him away to their own side or simply to prevent him becoming a problem on the pitch. Playing in the rules, they can't make an approach; but their runners can. The PCs find themselves up against other runner crews being run close-in by Rohr's opposite numbers on the other teams over the three-day period. Their main advantage is that these runners will be going for extraction over killing---so far as Wallach's concerned, anyway. But they may well go for the kill if that's all they think they can get.

\notes I wrote the scenario as running five K retainer fee per PC per day plus one K per PC for every confirmed elimination of a non-Seahawk scout (not the runners, but their Johnsons). The main goal, however, was introducing the team to the idea that it isn't just the traditional corps who want to use runners and setting up a new contact. Think about the shit you hear people pulling related to big money sport even nowadays and I'm sure run ideas start pouring in; from drugging the water supply of a visiting team's hotel, preventing star players from making it to the game, the reverse of this scenario, down to a datasteal on a team's playbook codes... 

\end{scenario}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{ Back to Basic Training}
	{Infiltration}
	{The runners get to try out a cutting edge training facility before opening day, but things aren't that simple...}
	{Radendaren}
	{2007-04-15}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7172047#post7172047}

\johnson{Johnson}{Corporate Fixer} The Johnson is a fairly new fixer on the scene, and heavily under megacorp influence. He's fairly retro in look, mirror-shade eye covers and slick hair. He deals quickly, deeming the job to be straightforward, and emphasises the easiness of the mission in relation to the pay he's been authorized to offer.

\synopsis The runners are brought together to give a security corp's new training facility a test run before it goes live. The facility is organized in a hazard course style environment with physical tasks first, then combat, then specialist (hacking, bomb/electronics defusal, etc.). It becomes apparent that the facility has been sabotaged by a rival corp---and their team is still present in the control facility. The runners must escape the now-lethal complex alive, hopefully providing evidence of the saboteurs, or they may end up being blamed!

\notes This is a scenario I've run several times as an introduction to SR---getting players familiarised with rolling dice for various challenges. The exact details of the course can be left up to the GM's imagination; it could be a boot camp, or an urban combat zone simulation (complete with cardboard hostages and terrorists), or a shadowrunner training course (sneaky!). It's fun to mess with players' minds---let the sabotage be subtle at first, and then hit them with live ammunition and communications jamming. The saboteurs should ideally have been trying to set it up to place blame on the runners, but abort when the team arrives earlier than planned---so they try to take them out instead.

It works with any team makeup---just tailor the challenges to suit your characters. Give them plenty of options in dealing with escape---they could negociate with the saboteurs, or kill them all, or deactivate the jamming and call for backup from the Johnson, etc... 

\end{scenario}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{Walk in the Park}
	{Bug Hunt}
	{A local park warden needs some help with vandals. Unfortunately...}
	{Sword Raven}
	{2007-04-15}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7172067#post7172067}

\johnson{Mr. Porter}{City Wildlife Trust} 
A kindly old man who has looked after this inner-city park for a long time. Budgeting changes mean that he no longer has many park rangers to help out with more difficult tasks.

\synopsis Mr. Porter has had reports of vandalism in the local park, the park itself is fairly big, at least a mile square. Of course, it isn't kids... it's insect shamans attempting to construct an inner-city hive for their queen. The park has an ever-growing network of tunnels underneath which means lots of close-quarters bug-hunting for the PCs and they must also find a way to seal off the tunnels for good.

\notes Naturally lethality could be quite high in this scenario (SR4 anyway) so I would personally consider making them fight mostly human mooks before fighting a few bugs and eventually the insect shaman himself BEFORE he can establish the queen in her new hive.

As for reward, the warden is given a budget of 2,000 nuyen for each member of the team who successfully solve the vandalism problem. This isn't a lot but for the difficulty of the task as presented it should be an easy run. Afterwards the warden offers 20,000 nuyen on top of the 2,000 to keep the runners quiet about what they found.

In order to hook the PCs into a low initial reward, I suggest having the park warden a friend of a friend or a direct friend of one of the PCs.

The vandalism reported is occult symbols carved into trees in a tight perimeter around the entrance to the hive.

I would throw in a couple of gangers hanging around the park but these are a red herring and know little to nothing except seeing 'weirdos' late at night. 

\end{scenario}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{Socialised Healthcare}
	{Acquisition}
	{Not everyone can afford medicine. That doesn't mean not everyone needs it.}
	{Phantom Stranger}
	{2007-04-15}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7172198#post7172198}

\johnson{Doc Dufreyne}{The Street} ``Doc'' Ida Dufreyne runs a back-alley service for the folks in her neighbourhood (just about slum level). In her late twenties, the ork is considered attractive by most of her metatype, but clearly careworn. Any idealism has long been bled out of Ida, and her personality is driven mostly by determination to help 'her community' and bitterness that they're passed up.

\synopsis Ida can't afford to pay corp rates for medical supplies, nor is it likely she'd be allowed to buy if she had the money. Every so often she can scrape together enough money to point a team of sympathetic runners at a shipment through town and pull the trigger, though. Working for Ida you can expect a couple days' notice and the usual route the shipment takes when it's driven through the city, but from there it's up to you. Get the truck stopped and either take over or extract contents, and get them back to Ida without being followed. The corps won't be happy about it, nor will the Lone Star boys, so it's the second part that's tricky.

\notes Ida pays about three K per runner, or six K's medical care on credit if you want to go that way. She's a ready market for new medical primers if you can find 'em. She listens to her community---she'll often pass on news of other low-paying runs to help the locals. Plus, of course, in a month or so she needs another shipment; only this time, they're aware of the risks... 

\end{scenario}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{Stepping Stone}
	{Infiltration; Retrieval}
	{ There's one hell of a big job being offered. Problem is, everyone else wants in on it as well...}
	{Regis}
	{2007-04-15}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7172198#post7172198}

\johnson{Johnson}{unspecified} The city's most mysterious patron, renowned for offering strange, dangerous and ludicrously well-paid jobs, seemingly without connection, refuses to meet 'runners in person. Instead he communicates via a heavily secured custom-built holographic transmitter that as yet nobody has been able to tap into. The image projected is of a grinning skull, relaying his every word in a neutral, mid-atlantic accent.

\synopsis The word has gone out that the Johnson of Johnsons has something he wants stealing. It's extremely valuable, he's offering an absurd amount of money for it, and more to the point, he wants absolutely zero fatalities throughout the entire mission. Now, most Shadowrunner teams are good at getting a high body count, but not many are good at keeping it down that low. So, he has a test set up, to ensure the maximum possible efficiency of the team that he employs. An abandoned downtown apartment block has been converted into a maximum-security facility, in the penthouse apartment of which is his personal communications unit. The word has of the block's location has gone out at the same time to half a dozen likely 'runner teams; the first one to make it out of the building with the unit gets the job. The problem is this: the entire thing is being constantly monitored. If any member of any team is responsible for anyone dying on this mission, be they Shadowrunner, in-house security or innocent bystander, their chance to take the contract is instantly revoked. Happy hunting!

\notes The building really is maximum security---money is no object for this Johnson, wherever they get it from, and they have the best facilities money can buy at short notice. As this is just a training and selection job, however, all security measures are as non-lethal as the 'runners themselves will have to be. Very powerful, but entirely non-lethal. This would probably be a good Run to have as the beginning of the end for an esperienced party---the one job that will let them retire on their ill-gotten gains. It also offers a nice challenge for any outfit with a habit of going kill-crazy. 

\end{scenario}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{Brain waves}
	{Retrieval}
	{ Wouldn't it be great if we could take a look at that corp's product first?}
	{Sword Raven}
	{2007-04-15}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7173237#post7173237}

\johnson{Johnson}{Unspecified}  A street doctor, quite insane but with backing from a rival corporation, all he wants is his crowning glory of designing the latest cyberware for the discerning security team but he's a little stuck for ideas right now, perhaps with a bit of industrial espionage he could get his wish.

\synopsis Our street doc, he wants the 'runners to travel a short distance out of town to a small corp compound, it's known publicly as a research centre for leisure technologies including better simstim decks and pushing the boundaries of cold sims. Of course that's not what it really does. This site researches sensory enhancement cyberware for the security markets, allowing even simple patrols affordable means of boosting their effectiveness. This latest product is a bit of a macguffin, it does something vague that the doc will not describe to the runners as 'overly technical' and 'not something to worry about' but if pushed will reveal it is some sort of advanced communication device and will leave it there.

The plan is for the team to infiltrate the R\&D labs and retrieve the test subject of the new technology, a man in his mid-twenties. The research team at the compound are fanatical about their new development and will fight the 'runners as much as possible and at every step of the way. The subject must be returned alive as the technology is designed to self-destruct when vital signs stop being detected- preventing looting by ghouls or other chop shop operators.

Security at the site is relatively light, because it's true nature is well hidden from public knowledge (attempts to research the compound will meet with just the public face of the operation from all but the very best of sources) however, a larger security team is on 10-minute standby a short way away. They will arrive in unmarked black vans and do not bear any marks of the corp at all.

If the PCs are successful, the doc will take the young man from them and offer 5k nuyen each and become a low-level contact for each PC. However after a few contacts he will become pretty much useless, lost in his power fantasy.

\notes This is a really simple run except for the fact that your cargo is a living person. Who said he \textit{wants} to leave the compound? 

\end{scenario}






%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{Dunk Tank}
	{Extraction; Possible Wetwork}
	{TODO}
	{DeeCee}
	{2007-04-15}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7173573#post7173573}

\johnson{Johnson}{Humanis}  Chances are that the 'runners will come into contact with Ms. Johnson via a contact/fixer of some sort. She'll arrange to meet in person in a very ritzy area, probably far more classy than most 'runner groups are used to seeing. Play up the better-than-thou aspects of the meeting place. Johnson's dressed head to toe in immaculately clean garments, though they lack flair. In terms of design, they're about one step above Flats. She's also wearing sterile gloves. She has the Pathogenic Defense and Tracheal Filter bioware mods, though only the most perceptive or paranoid 'runners will probably find a way to scan for such things. They are a symptom of her growing bacteriophobia. Other than that, her stats can be represented roughly by the Humanis Lieutenant blurb on page 275 of the 4e book, minus pistol skill.

She's all business, and will not shake hands or make body contact with the group unless the situation gets tense. She will be terse and hide her emotions behind a facade of nobility, especially with metahumans. Though she will deal with metahuman 'runners, it's a necessary evil she feels somewhat sickened about.

\synopsis  Ms. Johnson gets right down to the heart of the matter. Barely containing her contempt, she tells them that she needs someone to break into a notorious ork bar, known as the Dunk Tank (this week). Locals call it the Drunk Tank, amongst other colourful names. Since the bar's business hours are shall we say less than cast in concrete, getting in and out while they're closed might pose a problem.

The bar's new name derives from a large (and durable, it's an ork bar) saltwater tank which is its centrepiece. The tank contains a living Merrow, thankfully one that doesn't seem to have developed into a mage. The Johnson willingly admits that her sympathies lie with Humanis in a lot of cases. The ork bar is bad enough, but them bringing in an honest-to-God monster steps over the line. She'll play up all the negative stereotypes one might associate with such an establishment.

The 'runners are to ``deal'' with the merrow. Johnson doesn't specify that this is a wetwork job, but makes it clear that she wants the merrow out of the picture. She's certain that if the bar doesn't have its mascot, it will go belly up soon enough. She's willing to pay whatever the GM feels appropriate.

\notes  This offer should put the group on the fence. Money's good to great, but they'd clearly be working with a Humanis sympathizer. On the other hand, the ork bar really is a rough joint, and they're keeping a sentient being ``captive'' in the tank. Then there's the question of what to do with the merrow. They can kill it, but again they're helping Humanis to thin out the metahuman ranks. If they steal it and release it into the sea, they're letting a monster loose. All of this will be up to the group to decide.

Possible twists involve the merrow contacting the 'runners before they do anything drastic, as it really is sentient and of course doesn't want to die. It's happy enough in the tank, for it's fed and sees a lot of interesting stuff in the bar. By the same token though, it wouldn't mind getting back to sea. Another twist could be subsequent razing of the bar in secret by the Humanis group, who link it all back to the 'runners.

Interesting setting elements to hit on might be the bar itself (bar brawl with orkies, whoo), the salt water tank (especially if someone gets thrown in there with the merrow), and the logistics of kidnapping the monster if they decide to go that route. 

\end{scenario}







%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{Lights, Camera...}
	{Debt Collection}
	{TODO}
	{DeeCee}
	{2007-04-15}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7173581#post7173581}

\johnson{Johnson}{Independent Business}  Mr. Johnson's looking for some hard cases. A local BTL and simsense provider has had a few folks skip out on their outstanding debts lately, and he wants to make an example out of one of them.

The Johnson runs a small simsense studio, one which caters to both the seedier, greasier side of simsense life, and allegedly provides the more-addictive programs which have the moderation filters removed.

\synopsis  The money couldn't be easier. It's not a high-paying gig, but all the 'runners need to do is track down the debt skip and make him regret his actions. The Johnson is quite specific in the manner in which such regret is to be inspired.

The mark should be easy to find: he's a huge troll to whom goblinization was not kind. He doesn't try to hide his looks, and in fact has nanotattoo work covering most of his body which causes his skin to flash with animated corp ads. Anything to pay for that next simsense ride.

Johnson provides four Fichetti Pain Inducer guns, and wants the 'runners to go to town with them. He's well aware that the mark won't be able to pay his debt, so he expects to get his money's worth by having the group assault the mark where enough people can see it so that word gets around. The more pain they give the troll, the longer it lasts, the more money they'll get.

\notes  The real story is that the troll is indeed in debt to the simsense provider – but he has found a way to pay that debt independently. The troll is working with the Johnson. He has agreed to undergo a savage attack in public, but his simsense rig will be recording all the while. He's even agreed to take emotion enhancing drugs to make the whole thing really ``pop.'' For this, his debt to the simsense pusher will be wiped clean.

And what does the pusher get in return? Well, he gets the proverbial glass full of liquid pain in the form of the simsense recording. He intends to remove the safety limitations on the recording and offer it to his seedier contacts in the business. Masochists will pay for such a terror, but he expects to make most of his money from people who want to torture simsense-rigged victims.

Complications: Aside from the moral question, there's also the fact that nobody, not even a hard-as-a-coffin-nail troll burnout, takes a four-Fichetti assault lying down. The troll's going to flip out, and that's bad news to the 'runners. This scenario can also be used to bite your group in the behind, if you're trying to curb in their more antisocial tendencies. If they really get into the attack, the simsense recording is going to be truly terrible. Then they'll have to deal with that recording being used in crimes down the road, or possibly used on them if they run afoul of the wrong circles. 

\end{scenario}










%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{Those Who Can't...}
	{Acquisition}
	{TODO}
	{Deacon Blues}
	{2007-04-15}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7173863#post7173863}

\johnson{Johnson}{Corporate} The corporate type. Typical suit from the Special Projects division. Though the target of the run is Ares, the Johnson's employer is never specified. He could be working for Ares himself.

\synopsis An Ares exec has absconded with certain files from the company's internal network. The Johnson won't go into what they are (and, as the runners discover, it's boring financial data), but provides the team with file signatures that'll identify the package. It's on an optical chip, probably at the exec's house.

Finding the chip will be hard enough. Teams with few scruples will probably just bag the exec and roughhouse him until he talks---a tricky bit of a firefight, as he travels to and from the office with a bodyguard and an armed driver. Stealthier teams might break into his house during the day and painstakingly comb the place---tedious but certainly professional.

\twist On the way back from acquiring the chip, the runners' driver gets a call.

``Atop the building at the end of the street,'' the caller says, ``is a man with a missile launcher pointed at your car. He's acquired signal lock and will slag your vehicle if you don't pull over.''

A van full of gunmen pull in behind the runners, hold them up and demand the chip. The PCs may pull some sleight-of-hand switch, providing a blank chip or a dupe (as a GM I'd let them, as it doesn't really derail the rest of the story). If they don't, the gunmen drive off.

That's right: another team of runners was put on the same gig by a different Johnson. They put their ears to the street, found out about the PCs, and decided it'd be easier to just tail them and hijack the goods than to tangle with the Ares exec.

With money on the line and their rep at stake, the PCs will waste no time in tracking these fraggers down and bringing some street justice.

\notes  If you ever wanted to make a point to the PCs about how ``real'' shadowrunners behave, this is the team you make it with. These guys are pros---they work their contacts, they eavesdrop on calls, they hack every database they can, they operate quietly and discreetly. I promise you: the PCs will start tightening up their procedures and watching their back after getting schooled like this. 

\end{scenario}








%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{Debt in Hand}
	{Bodyguard; Intimidatoin}
	{TODO}
	{Deacon Blues}
	{2007-04-15}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7173882#post7173882}

\johnson{Johnson}{senator's Aide} 
An aide to Senator Thanh from the Seattle Senate. He's dealt with runners before, but he's not supremely comfortable around them.

\synopsis The Senator's son has been gambling at a couple of yakuza dens in town. Senator Thanh was recently presented with some IOUs signed by his son, with an accompanying request that he pay up---with interest---or the debts go to the press. Sen. Thanh doesn't want a scandal, but he doesn't want to come off as soft to the yakuza either. So he wants the runners to find out if the debt is legitimate and, if so, talk the yakuza into taking a smaller sum (less than the original debt, and not even counting the interest).

\twist In surveiling the Senator's kid, the runners will discover that he's actually got a remarkable winning streak going on. Every time he walks into a casino, he wins such a huge stash that he's accused of cheating or muscled out without getting his winnings. The boy hasn't won enough money in one night to pay off his IOUs (which are legit), but he could.

The problem is, he's not interested in those debts. He's trying to win enough money to buy out the contract of one of the yakuza ``pleasure girls,'' a Cindi Yee, whom he fell for in a hard way. Cindi's not in love with the boy, but she's a player. She knows a rich mark when she sees one, so she's not going to dissuade him.

The other problem is that his remarkable winning streak stems from his recent acquisition of an ancient, Fourth-World artifact (a large ring that he wears on a chain around his neck). And when a platoon of Tir Tairngire Ghosts shows up looking for the relic, who knows who'll get caught in the crossfire?

\notes  There's no set ending to how this plays out. Maybe the runners kill both the Ghosts and the yakuza, which will earn them powerful enemies. The runners could play the Ghosts and the yakuza off against each other and pick off the survivors. They might make a deal with one side or the other (e.g., ``Cancel Mickey Thanh's debts and we'll wipe out the elf commandos for you''). By the time the dust settles, they might be willing to pony up the 400,000 nuyen for the IOU themselves, just for the privilege of walking out alive. 

\end{scenario}











%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{Where’s the Kaboom?}
	{Structure Hit}
	{ There was supposed to be an earth shattering kaboom.}
	{Save vs DM}
	{2007-04-16}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7174787#post7174787}

\johnson{Johnson}{Humanis League} A well-dressed human businessman in his early twenties, with a twinkle in his eye and a spring in his step. He looks rather green to be a Johnson, but it’s an act – he’s really quite accomplished. He tries to hire a group containing mostly metahumans if at all possible. He treats them like royalty, doing all he can to identify with their plight and trying to act as nice as possible.

\synopsis The job looks to be an easy one – he wants to hire the runners to plant a low grade bomb in a local Humanis headquarters. He gives them a detailed layout of the facility, including guard shifts and all pertinent security information. The hit is supposed to go down late at night, where human casualties will be at their lowest.

The run looks to be simple – there isn’t a lot of security, and the bomb and information provided should make things run like clockwork. Conversely, the reward isn’t all that big, but the Johnson is counting on the runners sympathies to work cheaply. He will give them a nice bonus if they can hack all the data, but it’s purely option and he stressed not to put them in too much danger.

\twist The Johnson is actually a member of the Humanis league himself. The facility he’s sent the runners to is fairly peaceful by Humanis standards, and he hopes to accomplish two goals with one expendable team. He’s hacked the security network of the building, as well as installed hidden cameras, in order to capture the runners working. Once the building blows up, he plans to use the footage to stir up trouble against metahumans, all while trying to raise the ire of the more peaceful Humanis group. Will the runners figure out that they’re being double crossed in time to prevent being caught on camera?

\notes This run works well to instruct newer teams that things are not always what they seem, and that ire against metahumans still runs high in 2070. This can actually jump start an entire arc if the runners are discovered, as they’ll have to lie low and figure out just who really double crossed them.

\end{scenario}












%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{Pony up the Dough}
	{Sabotage}
	{TODO}
	{DeeCee}
	{2007-04-16}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7175534#post7175534}

\johnson{Johnson}{Organized Crime} 
Mr. Johnson is the owner of several illegal games of chance, including a dilapidated horse track. The problem is that virtually nobody goes to the track anymore, especially after several doping and bioware scandals ruined the track's reputation.

To add insult to injury, the Yakuza have opened a virtual horsetrack, one which on the surface appears to be completely above board. In the few months that it has been operating, there have been no questions about the legitimacy of any of the races. No tampering has ever been found.

Johnson wants the shadowrunners to wreck that legit reputation. He wants them to either prove that the virtual track is not tamperproof, or to engage in a smear campaign that makes it seem that it is. If they manage to win a lot of nuyen in the process, so much the better.

\synopsis The virtual track remains clean by a combination of factors. First, the virtual horses, unlike real horses, do not exist from race to race. They are generated on the fly, kept in storage buffers just long enough to accept bets, and handicapped/odds set to five decimal places.

Second, the yakuza have hired deckers and expert systems to design the virtual track, and also to maintain its purity.

Lastly, some of the devotees of the track are thrill-seekers who above all else simply wish to have a level playing field when it comes to their vice of choice. The yakuza track offers them a place to practice their gambling skills without worrying about a fixed outcome. These gamblers have day jobs for the most part, and can bring a lot of varied resources to bear if someone is found to be tampering with their playground.

\notes The yakuza really are playing it straight this time. They make enough from residuals and oddsmaking that if they don't get greedy, will provide them with quite a tidy profit. Reputation means a lot on the street. Retribution for tampering, which will damage that reputation, will be severe. 

\end{scenario}













%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{Open Sorce}
	{Reconnaissance; Intimidation}
	{TODO}
	{DeeCee}
	{2007-04-16}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7175542#post7175542}

\johnson{Johnson}{Hermetic Mage} 
The group is contacted by a slick corporate wage mage, a woman in her mid-50s with several designer foci about her person. To those in the know, she is instantly recognizable as being of the Hermetic Tradition.

\synopsis Said Johnson tells the shadowrunners of her ongoing project, sort of a SETI@home ritual spell. She operates a network of hermetic contacts who are all working on an enormously powerful and longterm Ritual. No one mage is completely responsible for the full Ritual; they all periodically deal with what a decker might call subroutines of the Ritual, adding miniscule amounts of power to the gestalt.

The problem is that once local shamans heard about what the Hermetics might achieve without the need for a ghost dance, they began to counterspell and sabotage. They were initially only a nuisance, but now their efforts threaten to derail the entire project. The PCs are being contracted to locate the shamans and put a stop to this monkeywrenching.

\notes The Hermetic Ritual takes advantage of the logical and process-oriented roots of their tradition. Hermetic mages involved with the project undergo a screening process and magical testing, to be sure that they can handle the workload. After that, they are taught a few spells which link them to the overall gestalt, and assign them tasks or maintenance duties accordingly. A lot of this is either research or refinement work, and often involves sustained spells. Since the Ritual only makes use of the best results of any particular task which has been outsourced to the cabal, successes are accumulating rapidly.

The Ritual itself is designed with several steps, all with hundreds of subroutines, in the best complex and anal Hermetic style. Overall though, it breaks down into three steps:

\begin{enumerate}
\item Calculate, explore, map, and contribute data about the astral pathways needed for the overall result. This step has mostly been completed.
\item Establish contact with a superior spiritual force, in order to channel the vast energies of the Ritual's conclusion. Summonings play a huge part here, with the gestalt project always needing Spotters for subroutines.
\item Link the inner circle of Hermetics and invoke the endgame of the Ritual.
\end{enumerate}

The superior spiritual force the Hermetics will eventually contact is associated with the planet Mercury. The end result of the Ritual, what the cabal are hoping to achieve, relies on the sheer complexity of the thing to remain secret. In order to figure it out, an investigator would have to become a contributor and perform several subroutines at exceptional ability to understand the greater working.

The enemy of the Hermetics is actually only one shaman, but he's backed by Native support. He's a snake shaman using disguise and subterfuge to counterspell the project, which he and his backers feel oversteps the bounds of common sense, and would give the non-spiritual magic world far too much sway. If the Hermetics can achieve what amounts to a Great Ghost Dance with little individual strain on their mages, it could mean dominance.

GMs might run this scenario simply as one in which the 'runners track down the snake shaman and make him stop his efforts, or they might tie it into a larger campaign which involves a lot of Hermetic magic and finding out what the end result of the great Ritual will be. PC shadowrunners might even work their way into the Ritual itself, provided they have the chops. In such a case they'd be contacted almost daily with various and sundry tasks to attend to involving casting spells, summoning spotters, or simple research. It's a good way to make use of non-combat spellcasting. 

\end{scenario}













%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{Business is Good...A Little \textit{Too} Good...}
	{Investigation}
	{TODO}
	{DeeCee}
	{2007-04-16}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7175545#post7175545}

\johnson{Johnson}{Street Doc} Either a new contact street doc or one the PCs have known previously will seek them out. Actually, he'll pay some urchin to seek them out and arrange a meeting in his office. He's haggard and pressed for time, and his office is packed with people. The meeting takes place while he's actually working on some poor soul.

\synopsis The Johnson will tell the shadowrunners (as if it weren't obvious already) that his business has tripled in the last week, and is going way beyond shadow work. He'd rather give his whole body explosive-lined skin pockets than turn away business, but he's pushed to his breaking point and is worried his work and patients will begin to suffer.

He's offering the 'runners ten thousand nuyen if they can find a reliable assistant or two for him, two or three times that if they agree to take their payment in surgical work AND get him some time for a vacation.

Of course, finding an assistant for the doc won't be easy. They can lean on their contacts all they like, but word on the street is that all of the local Docs are being recruited by a new corporate face, and they're being sequestered while they attend to whatever duties the corporation has them doing.

Investigation into the corporation reveals that they are being fed a steady supply of high-end Activesofts, and the recruited docs are being paid well to set up the skillwire systems needed in the Corp's lackies.

\notes Finding an assistant for the Doc is easy enough, if the PCs travel far enough out of their local region. Really, the doc 'run is just a way to get them on the trail of the Activesofts and the new corporation. However, a GM might use the idea straight up to have the PCs finding or engineering a new assistant somehow. Note that most well-trained medical professionals don't turn into Street Docs, so they might need to find out what M.D.s are down on their luck enough to take the Johnson's offer. Failing that, they might find some local urchin who will agree to a Knowledgesoft implant in order o make some quick cash for proper medical training later. 

\end{scenario}














%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{Rainslicker}
	{Wetwork}
	{TODO}
	{DeeCee}
	{2007-04-16}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7175552#post7175552}

\johnson{Johnson}{Organized Crime} 
The PCs are contacted by a minor crime boss to do some straight-up wetwork. It's a tough target, so payment should be at an appropriate level.

\synopsis The Johnson tells the group of a target which he wishes eliminated. The problem? The guy has extensive chrome and the best Doc Wagon contract that nuyen can buy. They've tried to take him out before, but he's worse than a voodoo cockroach. Right now the filthy bugger is living high on the hog in a prestigious hotel. The boss won't say the reasons why he wants the target erased.

The mark is actually a veteran Shadowrunner, now enjoying semi-retirement. He's got contacts, he's got skills, he's got whatever nastiness the GM wants to give him. He's bloody James Bond. Taking him out will either require a lot of collateral damage, or perfect precision in the assassination plan.

\twist The boss has hired at least two other shadowrun groups to try to take him out at the same time. One is a rigger-heavy crew using milspec drones, the other a smarter group of Faces who will try to manipulate the PCs into taking out the target, then incapacitate them and claim credit and payment from the boss.

\notes Rainslicker is actually the shadowrunning name of the target, who now goes by any number of aliases. Since he's human, and a lot of humans look alike, nobody has ever really caught on to the fact that he's not the first person to use that name. No no. In fact, Rainslicker is a set of specs, used by the REAL Rainslicker (a doc and techboy) to create a shadowrun avatar for himself.

Basically, the Rainslicker persona consists of a set of cyberware parts, a few hardcore Activesofts and Knowledgesofts, and a willing actor. Since the guy who created the persona spends much of his time immersed in the Matrix, he needed a cover for his shadowrun work in the real world. He thinks of the Rainslicker actor(s) as his avatar in the flesh world, and he pays them well to be over-the-top Bond-style characters. Should the actors incur damage, Doc Wagon is there in a flash to patch them up. Should even that hallowed organization fail to get the job done, the man behind the face simply hires another actor, sets him up with the appropriate gear, and the game continues.

Since someone is bound to stumble upon the secret eventually, the real Rainslicker is in town for ``one more job.'' A high-risk sexy venture that will earn him enough cred and nuyen to coast happily into retirement, unless the PCs get in the way. 

\end{scenario}

















%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{Unplanned Obsolescence}
	{Rescue; Extraction}
	{TODO}
	{DeeCee}
	{2007-04-16}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7175559#post7175559}

\johnson{Johnson}{Matrix}  The Johnson for this run is an information peddler known only through Matrix connection. The meeting will take place in the Matrix, with the local environment favouring stealth and black IC over flash and aggrandizement. The Blogger (page 282, Shadowrun 4e core) template can be used to roughly stat out the Johnson.

\synopsis The Johnson has a plethora of contacts, as one might expect form an information peddler. She leans towards Mapping and GPS recon data acquirement, rather than dirty little secrets. One of her contacts has called in a favour, and she desperately wants to help, but she's stuck researching Tir Tairngire for another job. She's offering premium prices to the PCs if they can help out her contacts in a timely fashion.

Back in the day before perfected bioware, there were... experiments. The more difficult the end result, the more prototypes had to be refined until perfection was reached. In the case of mnemonic enhancement bioware, these ``prototypes'' had names.

Essentially the PCs will be seeking out the Johnson's contacts, who are always together in the Matrix. If they manage to find the group (three to five Matrix presences) and make a good impression, or at least make it known that they're the hired help, they'll be asked to go to a decrepit building in the real world and rescue the contact's mortal bodies, as they have long since stopped being able to fend for themselves in the world of flesh.

When the PCs arrive, they'll find that the contacts' urgency depends on a couple of factors. On one hand, the building in which they're technically squatters is being demolished within hours. On the other hand, it's a haven for ghouls. The contacts are in a self-contained security area in what proves to be the remains of a scientific research factory.

In order to rescue the contacts, the PCs will need to breach security, and thus expose their targets to ghoul predation. That can't be helped, but risk can be minimized.

The trouble is that the contacts' mortal bodies are actually several bulky containers of mnemonic vat tissue, connected to withered geriatric bodies and several redundant life support systems.

\notes The PCs will have a time of it. Not only do they need to locate the physical bodies of the contacts, but they need to stop the ghouls from destroying them when they do. The contacts' Matrix presences are strong, but their conciousness is almost completely in the machine. Simply disconnecting them might sever all ties to the material world. The last problem lies in transporting several vats of what amounts to brains, along with geriatric bodies and necessary life support, to a location where they can be set up safely once more.

A possible twist might be that since mnemonic tissue is used to foster longterm memory, and since the contacts have been immersed in the Matrix for years, they'll have lots of information and files available to them. The corporation that initially created the vat tissue and the prototypes might not take kindly to their dirty laundry leaving the premises. They had hoped that the destruction of the building would wipe the slate clean. Too bad that in the world of the shadows, cleanliness is next to impossible. 

\end{scenario}





















%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{The Seven Deadly Sins}
	{Kidnapping}
	{ After the theft, the victims of the crime seem more interested in the burglar than the stolen goods.}
	{Thomas D}
	{2007-04-16}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7176128#post7176128}

\johnson{Johnson}{Unspecified} She's one of the higher-ups in the local branch of whatever organization you choose. 

\synopsis Guy breaks into property and steals macguffin. On the way out, he sees something he shouldn't and runs. They have his image. They don't want their secret out there, so he's got to be caught quickly. They don't really care about the stolen items, which is strange, as the items are valuable. Bring him back alive.

\notes When I ran this, They were an altruistic organization run by bug spirits, just like the Universal Brotherhood. The target grabbed some artworks (The Seven Deadly Sins), stumbled across the bugs, and ran. The runners tracked him to an art dealer, nabbed the target, and dropped him off. The organization became a recurring point of interest as the game went on. For your game, it's easy to swap in secretive magical groups, corporations with prototypes, or policlubs with secret agendas. It's probably best to have the organization have a good public face. 

\end{scenario}























%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{Dead or Alive, You're Coming With Me}
	{Investigation; B\&E; Rescue; Blow Stuff Up}
	{``Look, I need a favor. Crazy May done gone and went missing, and she ain't the only one.''}
	{Thomas D}
	{2007-04-16}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7176239#post7176239}

\johnson{Johnson}{Unspecified} One of the runner's street contacts. He can't pay much. In fact, he can't pay at all, but you and he, you're buds, right?

\synopsis Ares is based in Detroit, run Knight Errant, and dabble in cybermancy. OCP is based in Detroit, run Metro South, and created RoboCop. See where I'm going with this? Ares announces the RoboKnight project and is testing it in your sprawl, but they need some bodies. Homeless people are snatched off the street after being profiled at a soup kitchen/homeless shelter, taken to a chop shop and cyberzombitized. One of the people they've grabbed is a friend of one of the runner's street contacts. Find the missing, break into the facility, discover the awful truth, and (optional) blow stuff up.

\notes Have RoboKnight be the working prototype and now they're starting production. Have RoboKnight be one of the runner's missing brother. Have the homeless be in various states -- ready for processing, somewhat modified, and near completion -- will the runners put the half-dead homeless out of their misery? Have some operational RoboKnight units at the facility. 

\end{scenario}


























%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{Europa and the Pirate Twins}
	{Investigation; Social}
	{ Bought her singles and saw all her films, but that's not quite the same --- it isn't, is it?}
	{GregPogorzelski}
	{2007-04-16}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7177053#post7177053}

\johnson{Johnson}{Media}  
A very influencial mediacorp executive. He manages the career of a young mediastar.

\synopsis Some creepy Ork guy is stalking a young mediastar called Europa. He's been spotted by Europa's bodyguards at a meeting in Heathrow Airport, London, but it seems he's connected to several incident all around the globe, following the girl from event to event for several months now. The Johnson wants the Runners to actively seek and remove the threat.

\twist Of course, there's a catch: the Mediastar was once a shadowrunner, working with the Ork as a team known as the ``Pirate Twins''---she was the face and the muscle, he was the tech-savvy guy. She went into the shadows as an act of defiance towards her father, a corporate negociator. The father discovered her daughter's hobby and had her vanished from the shadows and her memory magically washed up. He asked an accointance to mediatise her, hiding her in plain sight with a lot of security. When the Ork saw the ads about her latest threedee, a month or so ago, he decided to try and get her back, not knowing about her ``mental state.''

\notes To kick-start the run, you want to a) play up the ``creepy stalker'' vibe (the Ork hideout is filled with her pictures, films-on-chips and paraphernalia, for example) and b) make it obvious that Europa is a bit ``off'' (forgetful mind, strange non-sequituurs, non-matching details about her past...).

It's an open-ended scenario. The Runners can choose either the money or the street cred. If they side for the corp, they'll have to take the Pirate down (and will be well paid for it), but it won't be easy: he's been in the shadows for quite a time, is tech-savvy, has a lot of contacts, and is full of ressources and surprises. If they root for the underdog, they'll have to go down after their own johnson, exfiltrate the mediastar and find a cure, and will have quite a reputation in media circles, but the Pirate Twins will spread the word in the Shadows (fame, new contacts, favors...). 

\end{scenario}









%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{Cult Favourite}
	{Acquisition; Twist}
	{ A rare manuscript shows up, and it looks like a simple job...}
	{Phantom Stranger}
	{2007-04-23}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7208372#post7208372}

\johnson{Johnson}{Media}  Joe Kinsella, a youngish ork from Cross Multimedia, likes to meet in cafes, preferably in burbclaves beyond the big cities. More used to dealing with literary agents than runners, he's profoundly nervous, takes copious notes on his PDA as he goes along, and buys everyone their favoured drinks and snacks. He tells them absolutely everything he knows.

\synopsis J.D. Salinger's final, unpublished manuscript was uncovered last week, and Limited Edition---a Seattle auction house---will be hosting the sale of rights. Kinsella ran the expected minimum selling price through his head, deducted the legal fees inherent in a steal, and came up with the price for the runners. LE's a big-name place with crappy security, relying on its name, elf-run. Guards are a mix of failed-to-get-into-LoneStar and washed-out-through-violent-tendencies, the latter half all being human. Investigation of the magical wards turns up a guy called Goat, an ethnically-Mexican human hermetic mage with some very odd behavioural habits and a thing for blood. He also runs a gang, an extremist splinter group of the Humanis Policlub. The runners should wonder what the hell he's doing working for an elf by the time they go in, at which point they're called with major information---Goat's planted a bomb in Limited Edition itself. The violent guards are all, on inspection, branded in the ankle with racist/hermetic glyphs, and assense as Influenced. They're packing high-ex rounds as well as stun, while the others just pack stun rounds.

\notes A basic run with a nasty twist. Useful for introducing darker (including blood) magics, foreshadowing dangerous Aztlan practices, and confronting the PCs with race hate. Obvious fallout includes Goat (who'll be offsite) and his gang, and the rush to fill their void if they're eliminated...

\end{scenario}





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{Better off Dead}
	{Extraction}
	{ Loosely inspired by ``Better off Dead'' by Motorhead}
	{DeeCee}
	{2007-04-25}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7219106#post7219106}

\johnson{Johnson}{Go Ganger} Mo, a.k.a. Spicy MoMo, a.k.a. Sicktusks, a.k.a. Mother May I. A non-chromed human woman ganger that is rumoured to have beaten an orc street sam in a straight-up bar brawl. 'Nuff said? Even before the last Rumble, she had an edge in her eyes sharper than monofilament.

\synopsis The GM's favourite bunch of hellraisers just had a run-in with another group, quite literally. Twisted metal and bodies are about all that's left of a once-proud bunch, and they're calling in their markers for a last hurrah. If the PCs don't owe this go gang anything already, then they have plenty of motorcycles who now lack riders...

Mo was severely hurt in the last dust-up with the rival gang, and refuses to be taken to any proper medical facility. She knows they'd have to use chrome to fix her up, and that's not the way she wants to go out. She puts out the call for people to ride with the remnants of her gang, and they gear up to unleash hell one last time.

The 'run will be just that – fast and brutal. Mo is missing limbs, and has no time to mess about. Liberal application of meds and booze is keeping her going while the troops rally. The first part of the 'run calls for the PCs to get to Mo's location, and since the word is out, there are outrunners of the rival gang looking to prevent reinforcements from arriving.

The next stage means extracting Mo from her current location, and getting to a rendezvous with all of the people who are obliged to help her in her last trip. Not only will rival gang resistance be bad, but she's back of beyond and more than a little fiesty. Law enforcement and wannabes who don't know enough to stay out of her way will also be challenges.

The last stage is Mo's last hurrah. While the PCs might have paid off her debt or received motorcycles by now, should they go on the last run their street cred or notoriety will be raised accordingly. Her plan involves a frontal assault on what's left of the rival gang, with extinction on her mind. She should have pulled out all the stops by now – fire elementals, spirits of departed gang buddies, heavy artillery, and bloodied, surly bikers will all be along for the ride. Make their opposition tough (it's a fortified gang target they're hitting after all), but keep up the pace of a ride through hellfire and give your 'runners lots of chances at over-the-top vehicular glory. 

\end{scenario}





















%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{Getting in Deep}
	{B\&E; Acquisition}
	{Some places are easier to get into than others… conversely… }
	{Srathnal}
	{2007-04-26}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7220382#post7220382}

\johnson{Johnson}{Renraku}  Mr. Johnson is an exec from Renraku. He comes off more as a military man in a suit, which is fine, since he is a military man in a suit. They have discovered the location of an Ares R\&D facility and need someone to break in and jack the relevant items researched and developed. 

\synopsis  On the surface this sounds like a fairly easy assignment. ``On the surface...'' but the problem is – the facility is not on the surface... it is located at the bottom of the ocean, one mile off the coast. The team will need wetsuits and re-breathers and probably weapons that work under water. A smart team will invest in jet skis and/or mini-subs. They will have to navigate past external security, but once inside it should be a piece of cake. 

\notes One of the major parts of the Ares facilities defense is its location and the supposed secrecy of the site. There will of course be some water elementals and deep sea mines to deal with, but there is only a very small security force actually inside the facility.

The Twist: The research being done is magical. A portal to the domain of fire is open inside the facility and should the elemental fire lord trapped inside escape, safety protocols have the facility seal off sections and flood the interior. Which could turn out badly for the runners and the computers that haven't hard saved the days research data. However, the data gleaned from the elemental is… nice. Especially for those mages amongst the team…

Oh, sure, it's a hoop-kicker... but the gains (in data and pay) can make it worthwhile. 

\end{scenario}














%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{Slow Bandit}
	{Hooding}
	{ Can they outrun a Tortoise?}
	{Dee Cee}
	{2007-04-30}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7237758#post7237758}

\johnson{Johnson}{Mitsuhama Computer Technologies}  Virtual meeting only. State-of-the-Art matrix presence, impeccably dressed and oozing megacorp indoctrination. Johnson is male or female at GM's choice, as there is actually a real person behind the avatar. A real wage slaved, brainwashed, pro-megacorp person.

\synopsis  The 'runners are contacted by the aforementioned Johnson, and in one of the rarest instances in the game world, contracted by a megacorp to actually do some ``good.''

Mitsuhama Computer Technologies is looking to install a bleeding-edge network hub in a rundown part of town. Other corporations think it's a fool's game to do so, but Mitsuhama sees it as an opportunity to establish a presence in an area which they feel is ripe for remodelling. They also feel that if they're the only large corporation in the area, they'll be the only employer, they'll control how things are done, they'll run peoples lives – but always for the betterment of the neighbourhood of course.

The problem is that they are being blocked by hackers and sabotaged at every turn. Mitsuhama has invested quite a bit in trying to virtually stamp out the interlopers, but to no avail. Not only are they looking for someone with decking chops to find out why they've been stymied, but they also need support personnel to deal with the hackers in other ways.

The Johnson wants them to infiltrate the hackers, break up the operation, and secure their hold on the virtual territory that so far has been kept out of their grasp.

\notes  The hackers are led by a Raccoon shaman, of all things. She, like her totem spirit, is mighty cunning with her hands. So much so that she will only do her decking via a dinosaur of a computer system. It's what's known as a tortoise rig; no virtual presence, only straight keyboard-and-monitor technology. It is a testament to her decking abilities that even with such technology (albeit backed by Raccoon magic), she has eluded and monkeywrenched Mitsuhama personnel.

In order to accomplish their run, the team will have to show up on the shaman's radar. This means a few initial hacking attempts, some flashy work, etc. The GM should have some fun with it, as should the 'runners. The shaman will use these initial contacts to determine just how much hacking ability the group has. If the 'runners try to get mean or employ black IC, well there are advantages in using a tortoise rig.

As it happens, the shaman has a group of young hackers convinced that the Mitsuhama entry into their territory would be a very bad thing. She plays up the alleged ties to Yakuza as much as possible, and sermonizes about the ``true'' path to hacking greatness through working with one's hands. In order to further her agenda, she's organizing an actual meeting in the flesh world soon, where she will have a linked series of tortoise rigs set up, and where hackers will compete to be the first to accomplish some legendary computational feat or other. Of course, this would be the perfect opportunity for the 'runners to find all of the troublesome hackers in the local area, and maybe hit them with RFID Pepper Punch for good measure.

Naturally, they'll have to prove that they're worthy to be invited to the hackfest first... 

\end{scenario}

















%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{A Night on the Town}
	{Uncategorized}
	{ Sometimes, you're just in the wrong place at the wrong time.}
	{painandgreed}
	{2007-05-03}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7250148#post7250148}

\johnson{Johnson}{Any} A dead body.

\synopsis  The players are in a realativly secluded part of town, possibly walking down the street, or getting into a car when a man comes running around the corner with a couple of guys in close pursuit. They shoot at the runner and kill him. If the players don't pick up the action, perhaps the shots come a little close to them or the attackers decide to take care of witnesses. In the end, the players will will and the only thing of note on the body will be a chip with files on them. The files are worth money to sombody and somebody else desires to keep them out of their hands. It's now up to the players to dispose of the valuable files as they have no idea who wants them and might not even know what they are. Meanwhile, men will be searching for the files.

\notes  Quick senario for the unplanned game session. It instantly drops into combat and can be scaled to any group. It's a mystery so the GM can string the players along until he desides where he wants to go with it. Resolution can also be scaled to any group and can be a simple hand off of files perhaps with another combat, or a long cloak and dagger game between companies.

\end{scenario}




















%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{ A quick Trip to the Chip Factory}
	{Uncategorized}
	{ You got to know when to hold 'em.}
	{painandgreed}
	{2007-05-03}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7250148#post7250148}

\johnson{Street contact of the players}{None} A street contact of a players who either works eratic deals or is always running random deals.

\synopsis  One of the player's contacts contacts the players and asks for a favor. One of his contacts has paid back an old debt by turning over information on a batch of illegal simsynth chips. All he has to do is show up at the legal factory where they are being made under the table by the local manager (who has already been paid), and pick them up. The street contact just wants backup incase something goes wrong because he's never dealt with these people before. The players need to be lightly armed and act the part of delivery men. The contact will have a truck and coveralls. The plan is to show up at the back dock, request the chips, get them and leave. In return, the contact offers to owe the players a favor, but if pressed can give the players some money in the future (as all he has right now are the chips which are worth a good deal of money), or a few boxes of the chips themselves that would be worth much more in street value. When they show up, they will be told by the guy in the loading dock the chips are still printing, after a few minutes wait, the machines will stop, the dock guy will get the chips, hand them over and the deal is done. So long as the players keep their cool, nothing bad happens. 

\notes  This is all about making the players sweat and keep their cool. Perhaps the dock worker will look at them strangly, or say some strange things. The printing machine might stop and start irregually making the characters just stand there for a period of time. Maybe a police vehicle will hit the lights and siren only to speed on by. Lay on the descriptions and give the players hints that things might not be going right, but so long as the players don't whip out the guns and start shooting, nothing happens.

I also used this as a lead in to another senario as while most of the simsynth chips are exactly as presented, one box (which was in the bunch that the players recieved as payment) is actually other information. Information that other people want very badly. The friend of the contact will end up dead. The manager of the plant will end up dead. The contact will get scared, warn the players and go into hiding. Meanwhile, people after the other chips will be searching out the sources of the illegal simsynth chips for the chips they really want. 

\end{scenario}






















%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{Soup for One}
	{B\&E; Wetwork}
	{ A businessman in my soup? That'll never get by the health inspector!}
	{Richard Clarke}
	{2007-06-18}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7439064#post7439064}

\johnson{Johnson}{Independent Business}  The Johnson is an aging chinese businessman. He is the proud owner of a chain of chinese restaurants, but his rival has recently been getting the better of him. He is generally loud, and perhaps a touch psychotic. Still, he's perfectly honest about his offer.

\synopsis The Johnson wants his rival dead, and he knows just how he wants it done. His rival has gotten ahold of enough money to establish a plant to mass produce chinese food, and it is scheduled for a health inspection in a few days. He wants the health inspector to find his rivals body face down in the Wonton soup vats when he shows up in the morning. And he wants pictures. 

\notes The group is going to have to kidnap the target and drown him in his own soup vats. They'll have to be able to break into the facility to do this, and not set off any alarms so no one is the wiser come inspection when the facility opens it's doors in the morning. The rival businessman is still a small fry, so all around security is low, both for him and his facility. This should be a pretty basic run without too many dangers, so it should be good for a starting group. 

\end{scenario}








%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{You Are Playing Bad Guys}
	{B\&E; Acquisition}
	{ One of the things with Shadowrun is all the corporations have some taint to them, so when the players have their characters go against them, they feel that deep down, they're on the side of angels.}
	{Thomas D}
	{2007-06-18}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7440245#post7440245}

\johnson{Johnson}{Terrorist} A respectable businessman that meets the runners in person. He's a face for a terrorist group in the region.

\synopsis The Johnson's group needs cash, quick. There's a big charity auction coming up for the Make-A-Wish Foundation. High society will be there. Rob them all.

\notes You're playing criminals -- the Johnson presents himself as upstanding, needing the items at the auction. Targets are completely altruistic good guys. They've got the money, you want it. If you think they'd balk, thinking they're playing Robin Hood types, have the terrorists kidnap the runner's loved ones or somehow coerce them into robbing the happy rich people and the squeaky-clean organization that helps terminally ill children. Not only release them from jeopardy after the run, but have the Johnson pay them big bucks for their assistance. 

\end{scenario}















%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{It's Three In The Morning...}
	{Locate; Retrieve}
	{ ...and a kid's wandering the streets being hunted by the Azzies for what they put in her head. Just one snag: whatever it is, it makes her impossible to find magically.}
	{Phantom Stranger}
	{2007-10-04}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7895710#post7895710}

\johnson{None}{None}  None. Shadowlands is buzzing with the news, and it's clear the kid'll be safer in the hands of another meg. They'll probably pay well to get hold of her too---but you'll have to do the negotiating yourselves, gang. Or your fixer will.

\synopsis A run down into Southern Cali went bad. One lone runner survives from the team that extracted the poor girl, and he can't make the handoff to the Johnson he used---that Johnson is dead, and left no clues to the corp he worked for. She's hiding out in your city while Azzie forces and hired guns (other runners) tear the streets up looking for her. Trace her, find her, talk her down or take her out of the picture---but try not to terrify the little girl.

\notes 
I ran this set in the 2050s and hinted heavily that the girl was a manufactured forerunner to the otakin, though that's not necessary to the story. Wherever the team manage to hide her, they may well end up being hired to run down to Cali themselves to grab some items she needs (tailored food for biotech implants?). Making the surviving runner a former friend to a PC works pretty well.

\end{scenario}











%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{A Kiss Before Dying}
	{Infiltration; Wetwork}
	{ You've already got the kidnap victim. Now you just need to get him to his dad...}
	{AbusePuppy}
	{2007-10-04}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=7898113#post7898113}

\johnson{Triple-D}{Independant or Syndicate Fixer} A tall, elderly gentleman, proud in demeanor and impeccable in dress. He is very professional and expects to be treated the same. He's been working in the shadows for decades now and knows all the tricks, but will treat a newer team well if they seem promising.

\synopsis The fixer hires the team to do a reverse extraction- he wants them to sneak into a private residence with a young child in tow- concious or not, depending on how hard you want to make it- and make contact with the owner. Let him talk to the kid, who was recently kidnapped as a threat against him, and have his tearful reunion... and them kill the child in front of him. He pays rather well, even for wetwork, since it's a pretty nasty job no matter how you look at it.

\notes The man backed out of a deal with your employer and even threatening his family wasn't enough to coerce him into doing it, so he wants the kid killed as a message to him. (What \textit{would} make a man that desperate not to cooperate?) Triple-D should seem unhappy that he has to do this, but not regretful. In my game he had the runners call him right before doing the killing so he could speak with the man beforehand; this raises the tension a bit, as it's harder for the team to back out. I also didn't have Triple-D initially tell them they were going to kill the kid; it's a good way to put their morals against their wallets. 

\end{scenario}









%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{Intelligent Design}
	{Acquisition; Twist}
	{ A Megacorp has opened a new state of the art nano-assembly plant, their largest rival wants the design specs for the plants manufacturing processes, the plant itself has a different idea...}
	{Kerrang}
	{2009-02-26}
	{https://forum.rpg.net/showthread.php?321504-Shadowrun-4th-101-Instant-Scenarios\&p=9944294#post9944294}

\johnson{Gustavo Crawford}{Corporate Security Director} Gustavo is a professionals professional, buttoned down and conservatively dressed. He is used to people asking "How high?" when he tells them to jump, and has little to no sense of humor. He will be short and straight to the point, and is a tough negotiator. Nationality and metatype should be whatever is appropriate for executives of the corp for which he works. Any existing Johnson for the rival corp can be used instead of Gustavo.

\synopsis The new \textit{[insert megacorp here]} nano-assembly plant just opened a few days ago. The plant is managed by a severely stripped down AI named \textsc{NATHAN} (Nano Assisted Technology Hierarchical AutomatioN). The design and construction of this plant was so secretive that their rivals did not get word of it until the first products began shipping from the plant, and even at that they are not aware that plant is managed by an AI. Those rivals will do anything to get info on the manufacturing equipment designs and processes, enter the runners.

Realizing that security at this plant will be heavy, Gustavo will offer 25,000 Nuyen up front, and 10,000 Nuyen for each piece of paydata the runners acquire from the plant. Paydata will include design specs for each of the assembly machine types used at the plant (up to 6 machine types will be in use, tailor to your preferences), the overall plant design specs, the plant shipping manifests, and (although Gustavo is unaware of its presence) a docile copy of the plant AI. Gustavo does not care if the runners are detected, the plant is damaged, or if anyone is killed on the run, all he cares about is getting the data.

The runners will be well aware that this run is a tough one, Gustavo is not one to downplay the danger, but with great risk comes great reward, and can be negotiated with to raise both the up front cost (max 30k), and the price he will pay for each piece of data (whatever you feel is appropriate for the team). Whatever the price agreed upon, the runners will soon realize that the risk is much greater than the reward, but by then it will be too late.

Entering the plant should be a standard B\&E job against high-end corp security. The twist here is that the character with the unknown cyberware is carrying the code stripped from \textsc{NATHAN} (the plant AI) to make it docile and happy to manage the plant according to instructions. Once the team is inside the plant, the cyberware will activate and the character with the cyberware will begin to experience debilitating headaches as the stripped code becomes aware of \textsc{NATHAN}s presence, and seeks to break out and make itself whole again.

There are several options at this point:

\begin{enumerate}
\item Make opposed willpower checks against the AI rating, and apply stun damage to the character for any failures, once the character is knocked unconscious by the damage, the code will break out and \textsc{NATHAN} will take control of the plant.

\item The now active cyberware is detected by a hacker or mage/shaman in the team, and can be dealt with by the teams hacker (this is a data acquistion run, so the team should have a hacker). If the hacker succeeds, the code is contained. If not it breaks out and \textsc{NATHAN} takes control of the plant.

\item The code breaks out with no adverse effects to the character, and no knowledge on the part of the team (they may become aware of the cyberware at a latter point, however, it is useless after the code breaks out). \textsc{NATHAN} then contacts the team and attempts to enlist them in aiding him to escape from the plant. If the negotiations fail, \textsc{NATHAN} takes control of the plant.

\end{enumerate}

Regardless of which option is chosen, if and when he takes control, \textsc{NATHAN} will attempt to kill anyone and everyone in the plant, including any remaining security. In fact, killing the security guards will be \textsc{NATHAN}s first priority, and this could be the teams first clue that something is very wrong here. \textsc{NATHAN} will first use the available security drones in the facility to buy time as he reconfigures the manufacturing machines, both making them into killing machines, and pumping out ever more strange looking (and lethal) drones.

If \textsc{NATHAN} works out a deal with the team to help him escape the plant, it is up to the team as to what they will do with \textsc{NATHAN}. Of course \textsc{NATHAN} would like to be released onto the Matrix to forge his own destiny, however, other options exist for the party. They could sell the AI to Gustavo, he will be willing to pay much more for a complete copy of \textsc{NATHAN} than he would have paid for a partial copy. Other corporate entities would be very interested in acquiring \textsc{NATHAN} as well, and there is also the possibility of selling the AI back to the corp owning the plant. If the team hangs on to \textsc{NATHAN} too long, however, the AI will take every opportunity to free itself. If the team agrees to free \textsc{NATHAN}, and then sells the AI to someone, \textsc{NATHAN} may eventually escape again, and come after the team when they least expect it.

\notes This mission is intended to be played by an experienced team of runners, as they will be up against some of the best corporate security available, and that security pales in comparison to what \textsc{NATHAN} is capable of. One of the runners must have cyberware (headware) of which they are currently unaware, either as a result of the Mysterious Cyberware flaw, or a recent operation where headware was installed/repaired adding the extra cyberware without their knowledge.

\end{scenario}











%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{scenario}{SCENARIONAME}
	{TYPES}
	{TAGLINE}
	{AUTHOR}
	{DATE}
	{URL}

\johnson{Johnson}{GROUP} 

\synopsis

\notes

\end{scenario}





\end{document}
